---
title: "Muss_PCA_GLM_DMX_Benthic"
author: "Rachael Blake"
date: "September 16, 2016"
output: html_document
---

```{r, echo=FALSE, include=FALSE}

# load necessary packages
library(randomForest) ; library(plyr) ; library(dplyr) ; library(psych) ; library(nlme) ; library(ggplot2) ; library(AICcmodavg) ; library(stats) ; library(ggfortify) ; library(devtools) ; library(tibble)

# load data 
BenNearMuss <- read.csv("C:/Users/rblake/Documents/NCEAS/GoA Dynamics WG/dmx-drivers/BenthicNearshore_MusselQuestData.csv")

# call the data assembly script
#source("Benthic_Nearshore_Drivers/Benthic_Nearshore_Data_.R")
#head(BenNear)

```

```{r, echo=FALSE}
# filtering data for more complete dataset
BenNear_m <- BenNearMuss %>%
             filter(Year %in% c(2005:2013),
                    Region %in% c("WPWS","KATM","KEFJ")) %>%
             mutate_each(funs(as.numeric), Otter_Abun_est) %>%
             mutate(log_mussel_Per_Cov = log(mussel_Per_Cov+1),
                    log_SOf_MusselSumBmss_gWW = log(SOf_MusselSumBmss_gWW+1),
                    log_TotChlA_micgL_FlMn = log(TotChlA_micgL_FlMn+1),
                    log_TotChlA_micgL_AnnMn = log(TotChlA_micgL_AnnMn+1)) %>%
             select(-BLOY_MnDensity_km2, -TotChlA_micgL_SpMn)

```

```{r, echo=FALSE}
#### Manipulate data columns to add 1-year lags!!!!

#dplyr::lead
#Copy with values shifted by 1.
#dplyr::lag
#Copy with values lagged by 1.

BenNear_reg_l <- BenNear_m %>% 
                 select(-Site_Name,-Quadrat,-Lat,-Long) %>%
                 group_by(Year, Region) %>%
                 summarise_each(funs(mean(., na.rm=TRUE))) %>%
                 ungroup() %>%
                 arrange(Region, Year) %>%
                 group_by(Region) %>%
                 mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
                        LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
                        LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
                        LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
                        LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
                        LAG_PDO_anul_mn = lag(PDO_anul_mn),
                        LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
                        LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
                        LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
                        LAG_SC_Mn_FWDisc_AnMn = lag(SC_Mn_FWDisc_AnMn),
                        LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
                        LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
                        LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn)) %>%
                 ungroup() 
               

# BenNear_GOA_l <- BenNear_m %>% 
#                  select(-Site_Name,-Quadrat,-Lat,-Long,-Region) %>%
#                  group_by(Year) %>%
#                  summarise_each(funs(mean(., na.rm=TRUE))) %>%
#                  ungroup() %>%
#                  arrange(Year) %>%
#                  mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
#                         LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
#                         LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
#                         LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
#                         LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
#                         LAG_PDO_anul_mn = lag(PDO_anul_mn),
#                         LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
#                         LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
#                         LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
#                         LAG_SC_Mn_FWDisc_AnMn = lag(SC_Mn_FWDisc_AnMn),
#                         LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
#                         LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
#                         LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn))    


```

###H1: Mussel recruitment (via abundance) is associated with strong wind stress periods (monthly average - and some metric of oscillations? freq?).

###H2: Mussel recruitment (via abundance) is associated with high Chl years - specifically the spring bloom.

###H3: Mussel recruitment (via abundance) is driven by extreme air temperatures – meaning degree heating days type of threshold plus time (needs to include tidal threshold). 



# Everything (or as much as possible)
```{r, echo=FALSE}
# Everyhting (or as much as possible) PCA
BenNear_reg_cpa <- BenNear_reg_l %>%  #filter(Year %in% c("2007","2010","2012","2013")) %>%
                   select(-mussel_Per_Cov, -Otter_Abun_est, -Otter_density_per_km2,
                          -WndDir_degT_AnnMn, -WndSp_m_s_AnnMn, -LAG_WndSp_m_s_AnnMn,
                          -WndDir_degT_Winter, -WndSp_m_s_Winter, -LAG_WndSp_m_s_Winter,
                          -WaterTmp_SpringAnom, -LAG_Bare_Sub_Per_Cov, -LAG_Fuc_dist_Per_Cov,
                          -LED_BLOYAdult_breed_n, -LED_SOf_MusselPropBmss,
                          -SOf_MusselSumBmss_gWW,-SOf_MusselPropBmss,
                          -log_SOf_MusselSumBmss_gWW, -TotChlA_micgL_AnnMn) %>% 
                   filter(complete.cases(.))

#data.frame(BenNear_reg_cpa[!complete.cases(BenNear_reg_cpa),])
```

```{r, echo=FALSE}
# Run the PCA
pca_cpa <- prcomp(~., data=BenNear_reg_cpa[,c(3:26,28:36)], na.action=na.omit, scale=TRUE)
#print(pca_cpa) # shows SDs and weightings
summary(pca_cpa)
#pca_cpa$x # this is the PCA scores for each row of data.
#pca_cpa$rotation  # weightings for variables by themselves
evyload <- abs(pca_cpa$rotation)
evi_per <- sweep(evyload, 2, colSums(evyload), "/")
evi_per_imp <- data.frame(evi_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
evi_per_imp2 <- data.frame(evi_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
evi_per_imp3 <- data.frame(evi_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
evi_per_imp4 <- data.frame(evi_per) %>% select(PC4) %>% tibble::rownames_to_column() %>%
               arrange(-PC4)
evi_per_imp5 <- data.frame(evi_per) %>% select(PC5) %>% tibble::rownames_to_column() %>%
               arrange(-PC5)
evi_per_imp ; evi_per_imp2 ; evi_per_imp3

par(mfrow=c(1,2))
plot(pca_cpa, main="everything")
plot(pca_cpa, type="lines", main="everything")

```

```{r, echo=FALSE}
# Plotting
pca_reg_all <- autoplot(prcomp(BenNear_reg_cpa[,c(3:26,28:36)], scale=TRUE),
                        data=BenNear_reg_cpa,  colour='Region', loadings=TRUE,
                        loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_all

```

```{r, echo=FALSE}
# GLM, comprehensive 
# subset the data based on above PCA
BenNear_reg_cpa_sub <- BenNear_reg_cpa %>%
                       select(log_mussel_Per_Cov,  
                              log_TotChlA_micgL_AnnMn, LAG_log_TotChlA_micgL_AnnMn, 
                              LAG_Ttl_FWDisc_Anom_AnMn, Ttl_FWDisc_Anom_AnMn, 
                              UpWelAnom_anul_mn, LAG_UpWelAnom_anul_mn, ENSO_fal_mn,
                              SOtt_AnnMnEngRec, Fuc_dist_Per_Cov, WaterTmp_C_Winter)
                              #PDO_anul_mn, LAG_PDO_anul_mn,
                              #PDO_winter_mn, SC_Mn_FWDisc_AnMn, LAG_SC_Mn_FWDisc_SpMn,
                              #NPGO_anul_mn, )
 
ev_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_cpa_sub, family=gaussian)
summary(ev_glm)


```

```{r, echo=FALSE}
# GLM, comprehensive 
# trying to get as many predictor variables in here as possible
BenNear_reg_cpa_sub2 <- BenNear_reg_cpa %>%
                        select(-Year, -Region, -UpWelAnom_fal_mn, -UpWelAnom_spr_mn,
                               -TotChlA_micgL_FlMn, -SC_Mn_FWDisc_SpMn, 
                               -Ttl_FWDisc_Anom_SpMn, -SC_Mn_FWDisc_FlMn, 
                               -Ttl_FWDisc_Anom_FlMn, -log_TotChlA_micgL_FlMn, 
                               -ENSO_spr_mn, -ENSO_fal_mn, -PDO_spring_mn, -PDO_winter_mn,
                               -WaterTmp_C_Winter, -LAG_log_TotChlA_micgL_AnnMn, 
                               -LAG_UpWelAnom_anul_mn, -LAG_PDO_anul_mn, 
                               -LAG_SC_Mn_FWDisc_AnMn, -LAG_Ttl_FWDisc_Anom_AnMn, 
                               -LAG_SC_Mn_FWDisc_SpMn, -LAG_Ttl_FWDisc_Anom_SpMn)
 
al_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_cpa_sub2, family=gaussian)
summary(al_glm)


```

```{r, echo=FALSE}
# GLM, comprehensive 
# everything with lags 
BenNear_reg_cpa_sub3 <- BenNear_reg_cpa %>%
                        select(log_mussel_Per_Cov, 
                               LAG_log_TotChlA_micgL_AnnMn, LAG_UpWelAnom_anul_mn, 
                               LAG_PDO_anul_mn, LAG_SC_Mn_FWDisc_AnMn,
                               LAG_Ttl_FWDisc_Anom_AnMn, LAG_SC_Mn_FWDisc_SpMn, 
                               LAG_Ttl_FWDisc_Anom_SpMn)
 
al2_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_cpa_sub3, family=gaussian)
summary(al2_glm)


```

```{r, echo=FALSE}

AIC(ev_glm, al_glm, al2_glm)

#names(BenNear_reg_cpa_sub2)

```



# "Climate" factor PCA
```{r, echo=FALSE}
# "Climate" factor PCA
BenNear_reg_pca <- select(BenNear_reg_l, log_mussel_Per_Cov, Region, 
                          LAG_UpWelAnom_anul_mn,
                          LAG_log_TotChlA_micgL_AnnMn, ENSO_anul_mn,
                          LAG_WndSp_m_s_AnnMn, LAG_Ttl_FWDisc_Anom_AnMn) %>%
                   filter(complete.cases(.))

#data.frame(BenNear_reg_pca[!complete.cases(BenNear_reg_pca),])
```

```{r, echo=FALSE}
# run the PCA
pca_cli <- prcomp(~., data=BenNear_reg_pca[,3:7], na.action=na.omit, scale=TRUE)
#print(pca_cli)
summary(pca_cli)
#pca_cli$x # this is the PCA scores for each row of data.  
cliload <- abs(pca_cli$rotation)
cli_per <- sweep(cliload, 2, colSums(cliload), "/")
cli_per_imp <- data.frame(cli_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
cli_per_imp2 <- data.frame(cli_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
cli_per_imp3 <- data.frame(cli_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
cli_per_imp ; cli_per_imp2 ; cli_per_imp3

par(mfrow=c(1,2))
plot(pca_cli, main="climate")
plot(pca_cli, type="lines", main="climate")


```

```{r, echo=FALSE}
# Plotting
pca_plot <- BenNear_reg_pca[,3:7]

pca_reg_cli <- autoplot(prcomp(pca_plot, scale=TRUE), data=BenNear_reg_pca, colour='Region',
                        #label = TRUE, label.size = 3,
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_cli

```


```{r, echo=FALSE}
# GLM, climate
# subset the data based on above PCA
BenNear_reg_pca_sub <- BenNear_reg_pca %>%
                       select(log_mussel_Per_Cov,  
                              LAG_UpWelAnom_anul_mn,
                              LAG_log_TotChlA_micgL_AnnMn, ENSO_anul_mn,
                              LAG_WndSp_m_s_AnnMn, LAG_Ttl_FWDisc_Anom_AnMn)
 
cl_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_pca_sub, family=gaussian)
summary(cl_glm)


```

```{r, echo=FALSE}

AIC(al_glm, cl_glm)

```




# "Biological" factor PCA
```{r, echo=FALSE}

BenNear_reg_bpc <- select(BenNear_reg_l, log_mussel_Per_Cov, Region, WaterTmp_C_AnnMn, 
                          WaterTmp_SpringAnom, Bare_Sub_Per_Cov, SOf_MusselPropBmss,
                          BLOYAdult_breed_n, Fuc_dist_Per_Cov) %>%
                   filter(complete.cases(.))

#data.frame(BenNear_reg_bpc[!complete.cases(BenNear_reg_bpc),])
```

```{r, echo=FALSE}
# run the PCA
pca_bio <- prcomp(~., data=BenNear_reg_bpc[,3:8], na.action=na.omit, scale=TRUE)
#print(pca_bio)
summary(pca_bio)
#pca_bio$x # this is the PCA scores for each row of data.  
bioload <- abs(pca_bio$rotation)
bio_per <- sweep(bioload, 2, colSums(bioload), "/")
bio_per_imp <- data.frame(bio_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
bio_per_imp2 <- data.frame(bio_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
bio_per_imp3 <- data.frame(bio_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
bio_per_imp ; bio_per_imp2 ; bio_per_imp3 

par(mfrow=c(1,2))
plot(pca_bio, main="biol")
plot(pca_bio, type="lines", main="biol")


```

```{r, echo=FALSE}
# Plotting
pca_plot_b <- BenNear_reg_bpc[,3:8]

pca_reg_bio <- autoplot(prcomp(pca_plot_b, scale=TRUE), data=BenNear_reg_bpc, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_bio

```

```{r, echo=FALSE}
# GLM, biological
# subset the data based on above PCA
BenNear_reg_bpc_sub <- BenNear_reg_bpc %>%
                       select(log_mussel_Per_Cov,  
                              WaterTmp_C_AnnMn, WaterTmp_SpringAnom, Bare_Sub_Per_Cov,
                              SOf_MusselPropBmss, BLOYAdult_breed_n, Fuc_dist_Per_Cov)
 
bo_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_bpc_sub, family=gaussian)
summary(bo_glm)


```


```{r, echo=FALSE}

AIC(al_glm, bo_glm)

```

# Wind Stress
```{r, echo=FALSE}

BenNear_wind <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov, WndSp_m_s_AnnMn,
                       WndSp_m_s_Winter, LAG_WndSp_m_s_AnnMn) %>%
                filter(complete.cases(.))

```


```{r, echo=FALSE}
# run the PCA
pca_wnd <- prcomp(~., data=BenNear_wind[,4:6], na.action=na.omit, scale=TRUE)
#print(pca_wnd)
summary(pca_wnd)
#pca_bio$x # this is the PCA scores for each row of data.  
wndload <- abs(pca_wnd$rotation)
wnd_per <- sweep(wndload, 2, colSums(wndload), "/")
wnd_per_imp <- data.frame(wnd_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
wnd_per_imp2 <- data.frame(wnd_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
wnd_per_imp ; wnd_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="wind")
plot(pca_wnd, type="lines", main="wind")


```

```{r, echo=FALSE}
# Plotting
pca_plot_w <- BenNear_wind[,4:6]

pca_reg_wnd <- autoplot(prcomp(pca_plot_w, scale=TRUE), data=BenNear_wind, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_wnd

```


```{r, echo=FALSE}
# GLM, wind stress
# 
BenNear_wind_sub <- BenNear_wind %>%
                    select(log_mussel_Per_Cov, WndSp_m_s_AnnMn,
                           WndSp_m_s_Winter, LAG_WndSp_m_s_AnnMn)
 
wind_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_wind_sub, family=gaussian)
summary(wind_glm)


```

#Chla
```{r, echo=FALSE}

BenNear_chla <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov,
                       log_TotChlA_micgL_AnnMn, LAG_log_TotChlA_micgL_AnnMn) %>%
                filter(complete.cases(.))

```

```{r, echo=FALSE}
# run the PCA
pca_chla <- prcomp(~., data=BenNear_chla[,4:5], na.action=na.omit, scale=TRUE)
#print(pca_chla)
summary(pca_chla)
#pca_chla$x # this is the PCA scores for each row of data.  
chlaload <- abs(pca_chla$rotation)
chla_per <- sweep(chlaload, 2, colSums(chlaload), "/")
chla_per_imp <- data.frame(chla_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
                arrange(-PC1)
chla_per_imp2 <- data.frame(chla_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
                arrange(-PC2)
chla_per_imp ; wnd_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="chla")
plot(pca_wnd, type="lines", main="chla")


```

```{r, echo=FALSE}
# Plotting
pca_plot_c <- BenNear_chla[,4:5]

pca_reg_chl <- autoplot(prcomp(pca_plot_c, scale=TRUE), data=BenNear_chla, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_chl

```

```{r, echo=FALSE}
# GLM, chlorophyll a
# 
BenNear_chla_sub <- BenNear_chla %>%
                    select(log_mussel_Per_Cov,  
                           log_TotChlA_micgL_AnnMn, LAG_log_TotChlA_micgL_AnnMn)
 
chla_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_chla_sub, family=gaussian)
summary(chla_glm)


```

# Water Temps
```{r, echo=FALSE}

BenNear_tmp <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov,
                      WaterTmp_WinterAnom, WaterTmp_C_Winter) %>%
               filter(complete.cases(.))

```

```{r, echo=FALSE}
# run the PCA
pca_tmp <- prcomp(~., data=BenNear_tmp[,4:5], na.action=na.omit, scale=TRUE)
#print(pca_tmp)
summary(pca_tmp)
#pca_tmp$x # this is the PCA scores for each row of data.  
tmpload <- abs(pca_tmp$rotation)
tmp_per <- sweep(tmpload, 2, colSums(tmpload), "/")
tmp_per_imp <- data.frame(tmp_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
                arrange(-PC1)
tmp_per_imp2 <- data.frame(tmp_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
                arrange(-PC2)
tmp_per_imp ; tmp_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="temp")
plot(pca_wnd, type="lines", main="temp")

```

```{r, echo=FALSE}
# Plotting
pca_plot_t <- BenNear_tmp[,4:5]

pca_reg_tmp <- autoplot(prcomp(pca_plot_t, scale=TRUE), data=BenNear_tmp, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_tmp

```

```{r, echo=FALSE}
# GLM, temperature
# 
BenNear_temp_sub <- BenNear_tmp %>%
                    select(log_mussel_Per_Cov,  
                           WaterTmp_WinterAnom, WaterTmp_C_Winter)
 
temp_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_temp_sub, family=gaussian)
summary(temp_glm)


```

```{r, echo=FALSE}

AIC(al_glm, wind_glm, chla_glm, temp_glm)

```












