---
title: "Muss_PCA_GLM_DMX_Benthic"
author: "Rachael Blake"
date: "September 16, 2016"
output: html_document
---

```{r, echo=FALSE, include=FALSE}

# load necessary packages
library(randomForest) ; library(plyr) ; library(dplyr) ; library(psych) ; library(nlme) ; library(ggplot2) ; library(AICcmodavg) ; library(stats) ; library(ggfortify) ; library(devtools) ; library(tibble) ; library(pROC)

# load data 
BenNearMuss <- read.csv("C:/Users/rblake/Documents/NCEAS/GoA Dynamics WG/dmx-drivers/BenthicNearshore_MusselQuestData.csv")

# call the data assembly script
#source("Benthic_Nearshore_Drivers/Benthic_Nearshore_Data_.R")
#head(BenNear)

```

```{r, echo=FALSE}
# filtering data for more complete dataset
BenNear_m <- BenNearMuss %>%
             filter(Year %in% c(2005:2015),
                    Region %in% c("WPWS","KATM","KEFJ"), 
                    !(Site_Name %in% c("Northwest Bay", "Herring Bay-Southwest", "Herring Bay-Bear Cove",
                                       "Ninagiak Island", "Disk Island"))) %>%
             mutate_each(funs(as.numeric), Otter_Abun_est) %>%
             mutate(log_mussel_Per_Cov = log(mussel_Per_Cov+1),
                    log_SOf_MusselSumBmss_gWW = log(SOf_MusselSumBmss_gWW+1),
                    log_TotChlA_micgL_FlMn = log(TotChlA_micgL_FlMn+1),
                    log_TotChlA_micgL_AnnMn = log(TotChlA_micgL_AnnMn+1)) %>%
             group_by(Site_Name) %>%
             mutate(mussel_Site_mn = mean(log_mussel_Per_Cov, na.rm=TRUE)) %>%  # Get site mean across all years
             ungroup() %>%
             group_by(Year, Region, Site_Name, Quadrat) %>%
             mutate(mussel_Anom = log_mussel_Per_Cov-mussel_Site_mn) %>%  # calc anomalies
             ungroup() %>%
             select(-BLOY_MnDensity_km2, -TotChlA_micgL_SpMn, -mussel_Site_mn)

```

```{r, echo=FALSE}
#### Manipulate data columns to add 1-year lags!!!!

#dplyr::lead
#Copy with values shifted by 1.
#dplyr::lag
#Copy with values lagged by 1.

BenNear_reg_l <- BenNear_m %>% 
                 select(-Site_Name,-Quadrat,-Lat,-Long) %>%
                 group_by(Year, Region) %>%
                 summarise_each(funs(mean(., na.rm=TRUE))) %>%
                 ungroup() %>%
                 arrange(Region, Year) %>%
                 group_by(Region) %>%
                 mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
                 #        LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
                 #       # LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
                 #       # LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
                 #        LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
                 #        LAG_PDO_anul_mn = lag(PDO_anul_mn),
                 #        LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
                 #        LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
                 #        LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
                         LAG_SC_Mn_FWDisc_AnMn = lag(SC_Mn_FWDisc_AnMn)) %>%#,
                 #        LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
                 #        LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
                 #        LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn)) %>%
                 ungroup() 
               

```

###H1: Mussel recruitment (via abundance) is associated with strong wind stress periods (monthly average - and some metric of oscillations? freq?).

###H2: Mussel recruitment (via abundance) is associated with high Chl years - specifically the spring bloom.

###H3: Mussel recruitment (via abundance) is driven by extreme air temperatures – meaning degree heating days type of threshold plus time (needs to include tidal threshold). 



# Everything (or as much as possible)
```{r, echo=FALSE}
# Everything (or as much as possible) PCA
BenNear_reg_cpa <- BenNear_reg_l %>%  #filter(Year %in% c("2007","2010","2012","2013")) %>%
                   filter(!(Year == "2007" & Region == "KEFJ")) %>%  # Tom D says don't use this year/region
                   select(-mussel_Per_Cov, -Otter_Abun_est, -Otter_density_per_km2,
                          -WndDir_degT_AnnMn, -WndSp_m_s_AnnMn, #-LAG_WndSp_m_s_AnnMn,
                          -WndDir_degT_Winter, -WndSp_m_s_Winter, #-LAG_WndSp_m_s_Winter,
                          -WaterTmp_SpringAnom, #-LAG_Bare_Sub_Per_Cov, -LAG_Fuc_dist_Per_Cov,
                          -SOf_MusselSumBmss_gWW,-SOf_MusselPropBmss, -Ala_marg_Per_Cov,
                          -log_SOf_MusselSumBmss_gWW, -TotChlA_micgL_AnnMn) %>% 
                   filter(complete.cases(.))

#data.frame(BenNear_reg_cpa[!complete.cases(BenNear_reg_cpa),])

# make testing and training datasets 
#BenNear_reg_cpa_test <- sample_n(BenNear_reg_cpa, 5)

#BenNear_reg_cpa_train <- anti_join(BenNear_reg_cpa, BenNear_reg_cpa_test, by=c("Year", "Region")) 


```

```{r, echo=FALSE}
# Run the PCA
pca_cpa <- prcomp(~., data=BenNear_reg_cpa[,-c(1,2,34,37)], na.action=na.omit, scale=TRUE)
#print(pca_cpa) # shows SDs and weightings
summary(pca_cpa)
#pca_cpa$x # this is the PCA scores for each row of data.
#pca_cpa$rotation  # weightings for variables by themselves
evyload <- abs(pca_cpa$rotation)
evi_per <- sweep(evyload, 2, colSums(evyload), "/")
evi_per_imp <- data.frame(evi_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
evi_per_imp2 <- data.frame(evi_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
evi_per_imp3 <- data.frame(evi_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
evi_per_imp4 <- data.frame(evi_per) %>% select(PC4) %>% tibble::rownames_to_column() %>%
               arrange(-PC4)
evi_per_imp5 <- data.frame(evi_per) %>% select(PC5) %>% tibble::rownames_to_column() %>%
               arrange(-PC5)
evi_per_imp ; evi_per_imp2 ; evi_per_imp3

par(mfrow=c(1,2))
plot(pca_cpa, main="everything")
plot(pca_cpa, type="lines", main="everything")



# Re-run PCA with smaller number of variables?  Use cut-off of <90% explained variance


```

```{r, echo=FALSE}
# Plotting
pca_reg_all <- autoplot(prcomp(BenNear_reg_cpa[,c(3:26,28:36)], scale=TRUE),
                        data=BenNear_reg_cpa,  colour='Region', loadings=TRUE,
                        loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=4)
pca_reg_all

```

```{r, echo=FALSE}
# GLM, comprehensive 
# subset the data based on above PCA
# Scenario 1
BenNear_reg_cpa_sub <- BenNear_reg_cpa %>%
                       select(mussel_Anom,
                              log_TotChlA_micgL_AnnMn, LAG_SC_Mn_FWDisc_AnMn, SC_Mn_FWDisc_AnMn,
                              UpWelAnom_anul_mn, ENSO_anul_mn, NPGO_anul_mn, PDO_anul_mn, 
                              WaterTmp_C_AnnMn, SOtt_AnnMnEngRec, Fuc_dist_Per_Cov,
                              Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov, Red_alg_per_Per_Cov)
                       
ev_glm <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub, family=gaussian)
summary(ev_glm)


```

```{r, echo=FALSE}
# GLM, comprehensive 
# trying to get as many predictor variables in here as possible
# Scenario 2
BenNear_reg_cpa_sub2 <- BenNear_reg_cpa %>% 
                        select(-Year, -Region, -log_mussel_Per_Cov, 
                               -UpWelAnom_fal_mn, -UpWelAnom_spr_mn,
                               -TotChlA_micgL_FlMn, -SC_Mn_FWDisc_SpMn, 
                               -Ttl_FWDisc_Anom_SpMn, -SC_Mn_FWDisc_FlMn, 
                               -Ttl_FWDisc_Anom_FlMn, -log_TotChlA_micgL_FlMn, 
                               -ENSO_spr_mn, -ENSO_fal_mn, -PDO_spring_mn, -PDO_winter_mn,
                               -WaterTmp_C_Winter, -WaterTmp_WinterAnom, 
                               -Ttl_FWDisc_Anom_AnMn, -Red_alg_ann_Per_Cov, 
                               -PDO_anul_mn, -LAG_log_TotChlA_micgL_AnnMn,
                               -LAG_SC_Mn_FWDisc_AnMn
                               )
 
al_glm <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2, family=gaussian)
summary(al_glm)

##### Scenario 3
BenNear_reg_cpa_sub2l <- BenNear_reg_cpa %>% 
                        select(-Year, -Region, -log_mussel_Per_Cov, 
                               -UpWelAnom_fal_mn, -UpWelAnom_spr_mn,
                               -TotChlA_micgL_FlMn, -SC_Mn_FWDisc_SpMn, 
                               -Ttl_FWDisc_Anom_SpMn, -SC_Mn_FWDisc_FlMn, 
                               -Ttl_FWDisc_Anom_FlMn, -log_TotChlA_micgL_FlMn, 
                               -ENSO_spr_mn, -ENSO_fal_mn, -PDO_spring_mn, -PDO_winter_mn,
                               -WaterTmp_C_Winter, -WaterTmp_WinterAnom, 
                               -Ttl_FWDisc_Anom_AnMn, -Red_alg_ann_Per_Cov, 
                               -PDO_anul_mn, -log_TotChlA_micgL_AnnMn,
                               -SC_Mn_FWDisc_AnMn
                               )
 
al_glm_l <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2l, family=gaussian)
summary(al_glm_l)

##### Scenario 4
BenNear_reg_cpa_sub2pl <- BenNear_reg_cpa %>% 
                        select(-Year, -Region, -log_mussel_Per_Cov, 
                               -UpWelAnom_fal_mn, -UpWelAnom_spr_mn,
                               -TotChlA_micgL_FlMn, -SC_Mn_FWDisc_SpMn, 
                               -Ttl_FWDisc_Anom_SpMn, -SC_Mn_FWDisc_FlMn, 
                               -Ttl_FWDisc_Anom_FlMn, -log_TotChlA_micgL_FlMn, 
                               -ENSO_spr_mn, -ENSO_fal_mn, -PDO_spring_mn, -PDO_winter_mn,
                               -WaterTmp_C_Winter, -WaterTmp_WinterAnom, 
                               -Ttl_FWDisc_Anom_AnMn, -Red_alg_ann_Per_Cov, 
                               -PDO_anul_mn, -LAG_log_TotChlA_micgL_AnnMn,
                               -SC_Mn_FWDisc_AnMn
                               )
 
al_glm_pl <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2pl, family=gaussian)
summary(al_glm_pl)

##### Scenario 5
BenNear_reg_cpa_sub2a <- BenNear_reg_cpa %>%
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov
                                )

al_glm2 <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2a, family=gaussian)
summary(al_glm2)

##### Scenario 6
BenNear_reg_cpa_sub2al <- BenNear_reg_cpa %>%
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, LAG_SC_Mn_FWDisc_AnMn,
                                Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov
                                )

al_glm2_l <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2al, family=gaussian)
summary(al_glm2_l)


##### Scenario 7
BenNear_reg_cpa_sub2b <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                Bare_Sub_Per_Cov, Fuc_dist_Per_Cov,  WaterTmp_C_AnnMn, 
                                SOtt_AnnMnEngRec, BLOYAdult_breed_n, ENSO_anul_mn,
                                UpWelAnom_anul_mn, NPGO_anul_mn
                                )
 
al_glm3 <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2b, family=gaussian)
summary(al_glm3)

##### Scenario 8
BenNear_reg_cpa_sub2bb <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                NPGO_anul_mn, WaterTmp_C_AnnMn, ENSO_anul_mn, 
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3b <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2bb, family=gaussian)
summary(al_glm3b)

##### Scenario 9 
BenNear_reg_cpa_sub2bt <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                Bare_Sub_Per_Cov, NPGO_anul_mn, 
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                UpWelAnom_anul_mn
                                )
 
al_glm3bt <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2bt, family=gaussian)
summary(al_glm3bt)

##### Scenario 10
BenNear_reg_cpa_sub2bw <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                Bare_Sub_Per_Cov, NPGO_anul_mn, UpWelAnom_anul_mn, 
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                Whelk_Sum_n_m2, barnacle_Per_Cov
                                )
 
al_glm3bw <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2bw, family=gaussian)
summary(al_glm3bw)

##### Scenario 11 
BenNear_reg_cpa_sub2e <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                NPGO_anul_mn, WaterTmp_C_AnnMn,
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3e <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2e, family=gaussian)
summary(al_glm3e)

##### Scenario 12
BenNear_reg_cpa_sub2wt <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                NPGO_anul_mn, 
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3wt <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2wt, family=gaussian)
summary(al_glm3wt)

##### Scenario 13  ### WINNER!!!
BenNear_reg_cpa_sub2f <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                                NPGO_anul_mn, WaterTmp_C_AnnMn,
                                Red_alg_per_Per_Cov, 
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3f <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2f, family=gaussian)
summary(al_glm3f)


##### NOTE: If other scales come up with other "best" models, test it all all scale levels.  Also, 
##### test scenario 13 at other scales. 
##### Test model performance of the "best" model at each level on all levels.  
##### Test all scenarios from Region data at lower scales. 


AIC(al_glm, al_glm2, al_glm3)

anova(al_glm, al_glm2, al_glm3)

```

```{r, echo=FALSE}
#
prob2 <- predict(al_glm3f, BenNear_reg_cpa_sub2f)
df33 <- cbind(BenNear_reg_cpa[,c(1,2,37)], prob2)

qplot(data=df33, prob2, mussel_Anom, color=Region, size=3)
cor(prob2, BenNear_reg_cpa[,37])
#cor(BenNear_reg_cpa_sub2a[,1], BenNear_reg_cpa_sub2a[,3])

# Hand calculate things   # CURRENTLY NOT THE WINNING MODEL 13!  NEEDS TO BE REVISED. 
#al_glm2$coefficients
# mod2 <- al_glm2$model %>%
#         mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
#                fresh = SC_Mn_FWDisc_AnMn * -0.0006520642,
#                bare = Bare_Sub_Per_Cov * -0.0443574427,
#                NPGO = NPGO_anul_mn * 0.5163426933, 
#                Fucs = Fuc_dist_Per_Cov * -0.0135771762,
#                inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
#         select(chl, fresh, bare, NPGO, Fucs, inter) %>%
#         rowSums() 
# 
# cbind(df33, mod2)       

```

```{r, echo=FALSE}
# Figure
# BenNear_reg_l # has data through 2015
# df33$prob2 # predicted mussel data

fig1 <- ggplot() + 
        geom_point(data=BenNear_reg_l, aes(x=as.factor(Year), y=mussel_Anom, color=Region), size=4) +
        geom_point(data=df33, aes(x=as.factor(Year), y=prob2, color=Region), shape=17, size=4) + 
        xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                    "2013", "2014", "2015")) +
        theme_bw() + geom_hline(yintercept = 0, show_guide = FALSE)
  #      scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                 "2013", "2014", "2015"))
        
       
fig1

```

```{r, echo=FALSE}
# Figure

line_dat <- BenNear_reg_cpa %>% 
            select(Year, Region, mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
                   Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov) %>%
            group_by() %>%
            mutate(mean of bare, fuc, mussel_anom) %>%
            ungroup() %>%
            gather("Variable", "value", 3:8) %>%
            mutate(facet = ifelse(Variable %in% c("NPGO_anul_mn", "mussel_Anom",
                                                  "log_TotChlA_micgL_AnnMn"), "A", 
                           ifelse(Variable %in% c("Fuc_dist_Per_Cov", "Bare_Sub_Per_Cov"), "B", 
                           ifelse(Variable == "SC_Mn_FWDisc_AnMn", "C",""))))

######
fig2 <- ggplot(data=line_dat, aes(x=as.factor(Year), y=value, color=Variable)) + 
        geom_line(aes(group=Variable)) + facet_wrap(~facet, ncol=1, scale="free") + 
        
fig2

```



```{r, echo=FALSE}
# Trying to get 2014 and 2015 based on generating an "average" freshwater dischange value and using that
# BenNear_reg_l # has data through 2015

k <- mean(BenNear_reg_l$SC_Mn_FWDisc_AnMn, na.rm = TRUE)

BenNear_reg_klug <- BenNear_reg_l %>%
                    mutate(SC_Mn_FWDisc_AnMn_klug = ifelse(is.nan(SC_Mn_FWDisc_AnMn), 
                                                           9997.097, SC_Mn_FWDisc_AnMn)) %>%
                    select(mussel_Anom, log_TotChlA_micgL_AnnMn, #SC_Mn_FWDisc_AnMn, Year, Region,   
                    Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov, SC_Mn_FWDisc_AnMn_klug) %>%
                    filter(Year %in% c(2006:2015)) %>%
                    select(-Year, -Region)

#mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
#Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov

```

```{r, echo=FALSE}
####
prob3 <- predict(al_glm2, BenNear_reg_klug)   #prob2 <- predict(al_glm2, BenNear_reg_cpa_sub2a)
df34 <- cbind(BenNear_reg_klug[,c(1:3)], prob3)



# Hand calculate things
#al_glm2$coefficients
mod2 <- al_glm2$model %>%
        mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
               fresh = SC_Mn_FWDisc_AnMn * -0.0006520642,
               bare = Bare_Sub_Per_Cov * -0.0443574427,
               NPGO = NPGO_anul_mn * 0.5163426933, 
               Fucs = Fuc_dist_Per_Cov * -0.0135771762,
               inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
        select(chl, fresh, bare, NPGO, Fucs, inter) %>%
        rowSums() 

cbind(df33, mod2)   





qplot(data=df34, as.factor(Year), prob3, color=Region, size=3)
qplot(data=df34, as.factor(Year), mussel_Anom, color=Region, size=3)

```




















# "Climate" factor PCA
```{r, echo=FALSE}
# "Climate" factor PCA
BenNear_reg_pca <- select(BenNear_reg_l, log_mussel_Per_Cov, Region, 
                          LAG_UpWelAnom_anul_mn,
                          LAG_log_TotChlA_micgL_AnnMn, ENSO_anul_mn,
                          LAG_WndSp_m_s_AnnMn, LAG_Ttl_FWDisc_Anom_AnMn) %>%
                   filter(complete.cases(.))

#data.frame(BenNear_reg_pca[!complete.cases(BenNear_reg_pca),])
```

```{r, echo=FALSE}
# run the PCA
pca_cli <- prcomp(~., data=BenNear_reg_pca[,3:7], na.action=na.omit, scale=TRUE)
#print(pca_cli)
summary(pca_cli)
#pca_cli$x # this is the PCA scores for each row of data.  
cliload <- abs(pca_cli$rotation)
cli_per <- sweep(cliload, 2, colSums(cliload), "/")
cli_per_imp <- data.frame(cli_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
cli_per_imp2 <- data.frame(cli_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
cli_per_imp3 <- data.frame(cli_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
cli_per_imp ; cli_per_imp2 ; cli_per_imp3

par(mfrow=c(1,2))
plot(pca_cli, main="climate")
plot(pca_cli, type="lines", main="climate")


```

```{r, echo=FALSE}
# Plotting
pca_plot <- BenNear_reg_pca[,3:7]

pca_reg_cli <- autoplot(prcomp(pca_plot, scale=TRUE), data=BenNear_reg_pca, colour='Region',
                        #label = TRUE, label.size = 3,
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_cli

```


```{r, echo=FALSE}
# GLM, climate
# subset the data based on above PCA
BenNear_reg_pca_sub <- BenNear_reg_pca %>%
                       select(log_mussel_Per_Cov,  
                              LAG_UpWelAnom_anul_mn,
                              LAG_log_TotChlA_micgL_AnnMn, ENSO_anul_mn,
                              LAG_WndSp_m_s_AnnMn, LAG_Ttl_FWDisc_Anom_AnMn)
 
cl_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_pca_sub, family=gaussian)
summary(cl_glm)


```

```{r, echo=FALSE}

AIC(al_glm, cl_glm)

```




# "Biological" factor PCA
```{r, echo=FALSE}

BenNear_reg_bpc <- select(BenNear_reg_l, log_mussel_Per_Cov, Region, WaterTmp_C_AnnMn, 
                          WaterTmp_SpringAnom, Bare_Sub_Per_Cov, SOf_MusselPropBmss,
                          BLOYAdult_breed_n, Fuc_dist_Per_Cov) %>%
                   filter(complete.cases(.))

#data.frame(BenNear_reg_bpc[!complete.cases(BenNear_reg_bpc),])
```

```{r, echo=FALSE}
# run the PCA
pca_bio <- prcomp(~., data=BenNear_reg_bpc[,3:8], na.action=na.omit, scale=TRUE)
#print(pca_bio)
summary(pca_bio)
#pca_bio$x # this is the PCA scores for each row of data.  
bioload <- abs(pca_bio$rotation)
bio_per <- sweep(bioload, 2, colSums(bioload), "/")
bio_per_imp <- data.frame(bio_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
bio_per_imp2 <- data.frame(bio_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
bio_per_imp3 <- data.frame(bio_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
bio_per_imp ; bio_per_imp2 ; bio_per_imp3 

par(mfrow=c(1,2))
plot(pca_bio, main="biol")
plot(pca_bio, type="lines", main="biol")


```

```{r, echo=FALSE}
# Plotting
pca_plot_b <- BenNear_reg_bpc[,3:8]

pca_reg_bio <- autoplot(prcomp(pca_plot_b, scale=TRUE), data=BenNear_reg_bpc, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_bio

```

```{r, echo=FALSE}
# GLM, biological
# subset the data based on above PCA
BenNear_reg_bpc_sub <- BenNear_reg_bpc %>%
                       select(log_mussel_Per_Cov,  
                              WaterTmp_C_AnnMn, WaterTmp_SpringAnom, Bare_Sub_Per_Cov,
                              SOf_MusselPropBmss, BLOYAdult_breed_n, Fuc_dist_Per_Cov)
 
bo_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_reg_bpc_sub, family=gaussian)
summary(bo_glm)


```


```{r, echo=FALSE}

AIC(al_glm, bo_glm)

```

# Wind Stress
```{r, echo=FALSE}

BenNear_wind <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov, WndSp_m_s_AnnMn,
                       WndSp_m_s_Winter, LAG_WndSp_m_s_AnnMn) %>%
                filter(complete.cases(.))

```


```{r, echo=FALSE}
# run the PCA
pca_wnd <- prcomp(~., data=BenNear_wind[,4:6], na.action=na.omit, scale=TRUE)
#print(pca_wnd)
summary(pca_wnd)
#pca_bio$x # this is the PCA scores for each row of data.  
wndload <- abs(pca_wnd$rotation)
wnd_per <- sweep(wndload, 2, colSums(wndload), "/")
wnd_per_imp <- data.frame(wnd_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
wnd_per_imp2 <- data.frame(wnd_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
wnd_per_imp ; wnd_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="wind")
plot(pca_wnd, type="lines", main="wind")


```

```{r, echo=FALSE}
# Plotting
pca_plot_w <- BenNear_wind[,4:6]

pca_reg_wnd <- autoplot(prcomp(pca_plot_w, scale=TRUE), data=BenNear_wind, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_wnd

```


```{r, echo=FALSE}
# GLM, wind stress
# 
BenNear_wind_sub <- BenNear_wind %>%
                    select(log_mussel_Per_Cov, WndSp_m_s_AnnMn,
                           WndSp_m_s_Winter, LAG_WndSp_m_s_AnnMn)
 
wind_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_wind_sub, family=gaussian)
summary(wind_glm)


```

#Chla
```{r, echo=FALSE}

BenNear_chla <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov,
                       log_TotChlA_micgL_AnnMn, LAG_log_TotChlA_micgL_AnnMn) %>%
                filter(complete.cases(.))

```

```{r, echo=FALSE}
# run the PCA
pca_chla <- prcomp(~., data=BenNear_chla[,4:5], na.action=na.omit, scale=TRUE)
#print(pca_chla)
summary(pca_chla)
#pca_chla$x # this is the PCA scores for each row of data.  
chlaload <- abs(pca_chla$rotation)
chla_per <- sweep(chlaload, 2, colSums(chlaload), "/")
chla_per_imp <- data.frame(chla_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
                arrange(-PC1)
chla_per_imp2 <- data.frame(chla_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
                arrange(-PC2)
chla_per_imp ; wnd_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="chla")
plot(pca_wnd, type="lines", main="chla")


```

```{r, echo=FALSE}
# Plotting
pca_plot_c <- BenNear_chla[,4:5]

pca_reg_chl <- autoplot(prcomp(pca_plot_c, scale=TRUE), data=BenNear_chla, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_chl

```

```{r, echo=FALSE}
# GLM, chlorophyll a
# 
BenNear_chla_sub <- BenNear_chla %>%
                    select(log_mussel_Per_Cov,  
                           log_TotChlA_micgL_AnnMn, LAG_log_TotChlA_micgL_AnnMn)
 
chla_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_chla_sub, family=gaussian)
summary(chla_glm)


```

# Water Temps
```{r, echo=FALSE}

BenNear_tmp <- select(BenNear_reg_l, Year, Region, log_mussel_Per_Cov,
                      WaterTmp_WinterAnom, WaterTmp_C_Winter) %>%
               filter(complete.cases(.))

```

```{r, echo=FALSE}
# run the PCA
pca_tmp <- prcomp(~., data=BenNear_tmp[,4:5], na.action=na.omit, scale=TRUE)
#print(pca_tmp)
summary(pca_tmp)
#pca_tmp$x # this is the PCA scores for each row of data.  
tmpload <- abs(pca_tmp$rotation)
tmp_per <- sweep(tmpload, 2, colSums(tmpload), "/")
tmp_per_imp <- data.frame(tmp_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
                arrange(-PC1)
tmp_per_imp2 <- data.frame(tmp_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
                arrange(-PC2)
tmp_per_imp ; tmp_per_imp2 

par(mfrow=c(1,2))
plot(pca_wnd, main="temp")
plot(pca_wnd, type="lines", main="temp")

```

```{r, echo=FALSE}
# Plotting
pca_plot_t <- BenNear_tmp[,4:5]

pca_reg_tmp <- autoplot(prcomp(pca_plot_t, scale=TRUE), data=BenNear_tmp, colour='Region',
                        loadings=TRUE, loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=3)
pca_reg_tmp

```

```{r, echo=FALSE}
# GLM, temperature
# 
BenNear_temp_sub <- BenNear_tmp %>%
                    select(log_mussel_Per_Cov,  
                           WaterTmp_WinterAnom, WaterTmp_C_Winter)
 
temp_glm <- glm(log_mussel_Per_Cov ~ ., data=BenNear_temp_sub, family=gaussian)
summary(temp_glm)


```

```{r, echo=FALSE}

AIC(al_glm, wind_glm, chla_glm, temp_glm)

```












