---
title: "Muss_PCA_GLM_DMX_Benthic"
author: "Rachael Blake"
date: "September 16, 2016"
output: html_document
---



```{r, echo=FALSE, include=FALSE}

# load necessary packages
library(randomForest) ; library(plyr) ; library(dplyr) ; library(psych) ; library(nlme) ; library(ggplot2) ; library(AICcmodavg) ; library(stats) ; library(ggfortify) ; library(devtools) ; library(tibble) ; 
library(pROC) ; library(tidyr) ; library(tidyverse)

# load data 
BenNearMuss <- read.csv("C:/Users/rblake/Documents/NCEAS/GoA Dynamics WG/dmx-drivers/BenthicNearshore_MusselQuestData.csv")

# call the data assembly script
#source("Benthic_Nearshore_Drivers/Benthic_Nearshore_Data_.R")
#head(BenNear)

```

```{r, echo=FALSE}
# filtering data for more complete dataset
BenNear_m <- BenNearMuss %>%
             filter(Year %in% c(2005:2015),
                    Region %in% c("WPWS","KATM","KEFJ"), 
                    !(Site_Name %in% c("Northwest Bay", "Herring Bay-Southwest", "Herring Bay-Bear Cove",
                                       "Ninagiak Island", "Disk Island"))) %>%
             #mutate_each(funs(as.numeric), Otter_Abun_est) %>%
             mutate(log_mussel_Per_Cov = log(mussel_Per_Cov+1),
                    #log_SOf_MusselSumBmss_gWW = log(SOf_MusselSumBmss_gWW+1),
                    log_TotChlA_micgL_FlMn = log(TotChlA_micgL_FlMn+1),
                    log_TotChlA_micgL_SpMn = log(TotChlA_micgL_SpMn+1),
                    log_TotChlA_micgL_AnnMn = log(TotChlA_micgL_AnnMn+1)) %>%
             group_by(Site_Name) %>%
             mutate(mussel_Site_mn = mean(log_mussel_Per_Cov, na.rm=TRUE)) %>%  # Get site mean across all years
             ungroup() %>%
             group_by(Year, Region, Site_Name, Quadrat) %>%
             mutate(mussel_Anom = log_mussel_Per_Cov-mussel_Site_mn) %>%  # calc anomalies
             ungroup() %>%
             select(-mussel_Site_mn)

```

# Regional Scale Analyses

```{r, echo=FALSE}
#### Manipulate data columns to add 1-year lags!!!!

#dplyr::lead
#Copy with values shifted by 1.
#dplyr::lag
#Copy with values lagged by 1.

BenNear_reg_l <- BenNear_m %>% 
                 select(-Site_Name,-Quadrat,-Lat,-Long) %>%
                 group_by(Year, Region) %>%
                 summarise_each(funs(mean(., na.rm=TRUE))) %>%
                 ungroup() %>%
                 arrange(Region, Year) %>%
                 group_by(Region) %>%
                 mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
                 #        LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
                 #       # LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
                 #       # LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
                 #        LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
                 #        LAG_PDO_anul_mn = lag(PDO_anul_mn),
                 #        LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
                 #        LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
                 #        LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
                         LAG_FWDisc_MeanYearly_ft3s1 = lag(FWDisc_MeanYearly_ft3s1)) %>%#,
                 #        LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
                 #        LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
                 #        LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn)) %>%
                 ungroup() 
               

```

####H1: Mussel recruitment (via abundance) is associated with strong wind stress periods (monthly average - and some metric of oscillations? freq?).

####H2: Mussel recruitment (via abundance) is associated with high Chl years - specifically the spring bloom.

####H3: Mussel recruitment (via abundance) is driven by extreme air temperatures – meaning degree heating days type of threshold plus time (needs to include tidal threshold). 


```{r, echo=FALSE}
# Everything (or as much as possible) for the PCA
BenNear_reg_cpa <- BenNear_reg_l %>%  #filter(Year %in% c("2007","2010","2012","2013")) %>%
                   filter(!(Year == "2007" & Region == "KEFJ")) %>%  # Tom D says don't use this year/region
                   select(-mussel_Per_Cov, -WaterTmp_SpringAnom, 
                          #-Otter_Abun_est, -Otter_density_per_km2,
                          #-SOf_MusselPropBmss, -SOf_MusselSumBmss_gWW, -log_SOf_MusselSumBmss_gWW
                          #-WndSp_m_s_AnnMn, -WndDir_degT_AnnMn, -LAG_WndSp_m_s_AnnMn,
                          #-WndSp_m_s_Winter, -WndDir_degT_Winter, -LAG_WndSp_m_s_Winter,
                          #-LAG_Bare_Sub_Per_Cov, -LAG_Fuc_dist_Per_Cov,
                          -Ala_marg_Per_Cov, -TotChlA_micgL_AnnMn) %>% 
                   filter(complete.cases(.))

#data.frame(BenNear_reg_cpa[!complete.cases(BenNear_reg_cpa),])

# make testing and training datasets 
#BenNear_reg_cpa_test <- sample_n(BenNear_reg_cpa, 5)

#BenNear_reg_cpa_train <- anti_join(BenNear_reg_cpa, BenNear_reg_cpa_test, by=c("Year", "Region")) 


```

```{r, echo=FALSE}
# Run the PCA
pca_cpa <- prcomp(~., data=BenNear_reg_cpa[,-c(1,2,15,16,40)], na.action=na.omit, scale=TRUE)
#print(pca_cpa) # shows SDs and weightings
summary(pca_cpa)
#pca_cpa$x # this is the PCA scores for each row of data.
#pca_cpa$rotation  # weightings for variables by themselves
evyload <- abs(pca_cpa$rotation)
evi_per <- sweep(evyload, 2, colSums(evyload), "/")
evi_per_imp <- data.frame(evi_per) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
evi_per_imp2 <- data.frame(evi_per) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
evi_per_imp3 <- data.frame(evi_per) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
evi_per_imp4 <- data.frame(evi_per) %>% select(PC4) %>% tibble::rownames_to_column() %>%
               arrange(-PC4)
evi_per_imp5 <- data.frame(evi_per) %>% select(PC5) %>% tibble::rownames_to_column() %>%
               arrange(-PC5)
evi_per_imp6 <- data.frame(evi_per) %>% select(PC6) %>% tibble::rownames_to_column() %>%
               arrange(-PC6)
evi_per_imp7 <- data.frame(evi_per) %>% select(PC7) %>% tibble::rownames_to_column() %>%
               arrange(-PC7)
#evi_per_imp ; evi_per_imp2 ; evi_per_imp3

par(mfrow=c(1,2))
plot(pca_cpa, main="everything")
plot(pca_cpa, type="lines", main="everything")



# Re-run PCA with smaller number of variables?  Use cut-off of <90% explained variance


```

```{r, echo=FALSE}
# Plotting
pca_reg_all <- autoplot(prcomp(BenNear_reg_cpa[,-c(1,2,15,16,40)], scale=TRUE),
                        data=BenNear_reg_cpa,  colour='Region', loadings=TRUE,
                        loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=4)
pca_reg_all

```

```{r, echo=FALSE}
# Function to subset the dataframe and run the models and generate the outputs for comparison
data_sub_model_run <- function(orig_df, select_cols){
                               # subset the large regional dataframe for a given scenario
                               BN_reg_sub_df <- orig_df %>%
                                                select_(.dots=select_cols)
                               
                               glm_results <- glm(mussel_Anom ~ ., data=BN_reg_sub_df, family=gaussian)
                               glm_sum <- summary(glm_results)
                               small_summary <- list(glm_sum$aic, glm_sum$coefficients)
                               
                               return(small_summary)
  
}
  
```


##### Scenario 1 - Region
```{r, echo=FALSE}
# GLM, comprehensive 
# subset the data based on above PCA

# BenNear_reg_cpa_sub <- BenNear_reg_cpa %>%
#                        select(mussel_Anom,
#                               log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1, Hobo_WaterTemp_AnnMn,
#                               UpWelAnom_anul_mn, ENSO_anul_mn, NPGO_anul_mn, PDO_anul_mn, 
#                               WaterTmp_C_AnnMn, SOtt_AnnMnEngRec, Fuc_dist_Per_Cov,
#                               Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov, Red_alg_per_Per_Cov)
#                        
# ev_glm <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub, family=gaussian)
# sum_ev_glm <- summary(ev_glm)
# sum_ev_glm$aic
# sum_ev_glm$coefficients

##########
BenNear_reg_cpa_sub <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                         "Hobo_WaterTemp_AnnMn","UpWelAnom_anul_mn", "ENSO_anul_mn", "NPGO_anul_mn", 
                         "PDO_anul_mn", "WaterTmp_C_AnnMn", "SOtt_AnnMnEngRec", "Fuc_dist_Per_Cov",
                         "Brwn_alg_ann_Per_Cov", "Green_alg_ann_Per_Cov", "Red_alg_per_Per_Cov")

Sce_1 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub)
Sce_1

```

##### Scenario 2 - Region
```{r, echo=FALSE}
# GLM, comprehensive 
# trying to get as many predictor variables in here as possible

BenNear_reg_cpa_sub2 <- c("-Year", "-Region", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn",    
                          "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn",
                          "-TotChlA_micgL_SpMn", "-LAG_FWDisc_MeanYearly_ft3s1", "-ENSO_spr_mn",
                          "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn", "-WaterTmp_C_Winter",
                          "-WaterTmp_WinterAnom", "-Red_alg_ann_Per_Cov", "-PDO_anul_mn",
                          "-LAG_log_TotChlA_micgL_AnnMn", "-FWDisc_MeanFall_ft3s1", 
                          "-WaterTmp_C_AnnMn", " -Red_alg_per_Per_Cov", "-Neo_Odon_sp_Per_Cov",
                          "-FWDisc_MeanSpring_ft3s1", "-log_TotChlA_micgL_SpMn"
                          )

Sce_2 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2)
Sce_2

```

##### Scenario 3 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2l <- c("-Year", "-Region", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn",
                           "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn",
                           "-TotChlA_micgL_SpMn", "-log_TotChlA_micgL_SpMn",
                           "-ENSO_spr_mn", "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn",
                           "-WaterTmp_C_Winter", "-WaterTmp_WinterAnom", "-Red_alg_ann_Per_Cov",
                           "-Red_alg_per_Per_Cov", "-PDO_anul_mn", "-log_TotChlA_micgL_AnnMn",
                           "-WaterTmp_C_AnnMn", "-Neo_Odon_sp_Per_Cov", "-FWDisc_MeanSpring_ft3s1",
                           "-FWDisc_MeanFall_ft3s1", "-FWDisc_MeanYearly_ft3s1"
                           )

Sce_3 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2l)
Sce_3

```

##### Scenario 4 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2pl <- c("-Year", "-Region", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn", 
                            "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn", 
                            "-TotChlA_micgL_SpMn", "-log_TotChlA_micgL_SpMn", "-ENSO_spr_mn", 
                            "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn", "-WaterTmp_C_Winter",
                            "-WaterTmp_WinterAnom", "-Red_alg_ann_Per_Cov", "-Red_alg_per_Per_Cov",
                            "-PDO_anul_mn", "-LAG_log_TotChlA_micgL_AnnMn",  
                            "-LAG_FWDisc_MeanYearly_ft3s1", "-FWDisc_MeanSpring_ft3s1",   
                            "-FWDisc_MeanFall_ft3s1", "-WaterTmp_C_AnnMn", "-Neo_Odon_sp_Per_Cov"
                            )

Sce_4 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2pl)
Sce_4

```

##### Scenario 5 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2a <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov")

Sce_5 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2a)
Sce_5

```

##### Scenario 6 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2al <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "LAG_FWDisc_MeanYearly_ft3s1",
                            "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov"
                            )

Sce_6 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2al)
Sce_6

```

##### Scenario 7 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2b <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "Bare_Sub_Per_Cov", "Fuc_dist_Per_Cov",  "Hobo_WaterTemp_AnnMn",
                           "SOtt_AnnMnEngRec", "BLOYAdult_breed_n", "ENSO_anul_mn",
                           "UpWelAnom_anul_mn", "NPGO_anul_mn"
                           )

Sce_7 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2b)
Sce_7

```

##### Scenario 8 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2bb <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "ENSO_anul_mn", "Fuc_dist_Per_Cov",
                            "Red_alg_per_Per_Cov", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                            )

Sce_8 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2bb)
Sce_8

```

##### Scenario 9 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2bt <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov", 
                            "Red_alg_per_Per_Cov", "UpWelAnom_anul_mn"
                            )

Sce_9 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2bt)
Sce_9

```

##### Scenario 10 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2bw <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "Bare_Sub_Per_Cov", "NPGO_anul_mn", "UpWelAnom_anul_mn", 
                            "Fuc_dist_Per_Cov", "Red_alg_per_Per_Cov", "Whelk_Sum_n_m2", 
                            "barnacle_Per_Cov"
                            )

Sce_10 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2bw)
Sce_10

```

##### Scenario 11 - Region
```{r, echo=FALSE}
BenNear_reg_cpa_sub2e <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                NPGO_anul_mn, Hobo_WaterTemp_AnnMn,
                                Fuc_dist_Per_Cov, Red_alg_per_Per_Cov, 
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3e <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2e, family=gaussian)
summary(al_glm3e)

BenNear_reg_cpa_sub2e <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Fuc_dist_Per_Cov",
                           "Red_alg_per_Per_Cov", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                           )

Sce_11 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2e)
Sce_11

```

##### Scenario 12 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub2wt <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "NPGO_anul_mn", "Fuc_dist_Per_Cov", "Red_alg_per_Per_Cov", 
                            "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                            )

Sce_12 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2wt)
Sce_12

```

##### Scenario 13 - Region    WINNER!!!
```{r, echo=FALSE}

BenNear_reg_cpa_sub2f <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Red_alg_per_Per_Cov", 
                           "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                           )

Sce_13 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub2f)
Sce_13

```

##### Scenario 14 - Region
```{r, echo=FALSE}

BenNear_reg_cpa_sub14 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "NPGO_anul_mn", 
                           "Hobo_WaterTemp_AnnMn", "Red_alg_per_Per_Cov",
                           "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                           )

Sce_14 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub14)
Sce_14

```

##### Scenario 15 - Region
```{r, echo=FALSE}
BenNear_reg_cpa_sub15 <- BenNear_reg_cpa %>% 
                         select(mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                NPGO_anul_mn, Hobo_WaterTemp_AnnMn,
                                Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                )
 
al_glm3f_15 <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub15, family=gaussian)
summary(al_glm3f_15)

BenNear_reg_cpa_sub15 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Bare_Sub_Per_Cov", 
                           "UpWelAnom_anul_mn"
                           )

Sce_15 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub14)
Sce_15

```

##### Scenario 16  
```{r, echo=FALSE}

BenNear_reg_cpa_sub16 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                           "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Red_alg_TOT_Per_Cov",
                           "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                           )

Sce_16 <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_reg_cpa_sub16)
Sce_16

```

##### AIC values for all Regional models
```{r, echo=FALSE}
Reg_mod_list <- list(Sce_1, Sce_2, Sce_3, Sce_4, Sce_5, Sce_6, Sce_7, Sce_8, 
                     Sce_9, Sce_10, Sce_11, Sce_12, Sce_13, Sce_14, Sce_15, Sce_16)

for (i in 1:length(Reg_mod_list)) {
     print(Reg_mod_list[[i]][[1]])
     }

```

##### NOTE: If other scales come up with other "best" models, test it all all scale levels.   
##### Also, test scenario 13 at other scales. 
##### Test model performance of the "best" model at each level on all levels.  
##### Test all scenarios from Region data at lower scales. 

##### Site-level Scenario 15  # WINNER of the Site-level fitting
```{r, echo=FALSE}
# Comparing Scenario 15 from the Site-level model fitting exercise
BenNear_site_cpa_sub215_r <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                               "NPGO_anul_mn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                               )

Sce_15s <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_site_cpa_sub215_r)
Sce_15s

```

##### Transect-level Scenario 12   # WINNER from the Transect-level analysis
```{r, echo=FALSE}
# Comparing Scenario 12 from Transect-level model fitting exercise
BenNear_tran_cpa_sub2l12_r <- c("mussel_Anom", "log_TotChlA_micgL_FlMn", "FWDisc_MeanYearly_ft3s1",
                                "SOtt_AnnMnEngRec", "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn",
                                "BLOYAdult_breed_n", "Bare_Sub_Per_Cov", "Brwn_alg_ann_Per_Cov",
                                "Green_alg_ann_Per_Cov"
                                )

Sce_12t <- data_sub_model_run(orig_df=BenNear_reg_cpa, select_cols=BenNear_tran_cpa_sub2l12_r)
Sce_12t

```

```{r, echo=FALSE, eval=FALSE}
#
prob2 <- predict(al_glm3f, BenNear_reg_cpa_sub2f)
df33 <- cbind(BenNear_reg_cpa[,c(1,2,38)], prob2)

qplot(data=df33, prob2, mussel_Anom, color=Region, size=3)
cor(prob2, BenNear_reg_cpa[,38])
#cor(BenNear_reg_cpa_sub2a[,1], BenNear_reg_cpa_sub2a[,3])

# Hand calculate things   # CURRENTLY NOT THE WINNING MODEL 13!  NEEDS TO BE REVISED. 
#al_glm2$coefficients
# mod2 <- al_glm2$model %>%
#         mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
#                fresh = SC_Mn_FWDisc_AnMn * -0.0006520642,
#                bare = Bare_Sub_Per_Cov * -0.0443574427,
#                NPGO = NPGO_anul_mn * 0.5163426933, 
#                Fucs = Fuc_dist_Per_Cov * -0.0135771762,
#                inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
#         select(chl, fresh, bare, NPGO, Fucs, inter) %>%
#         rowSums() 
# 
# cbind(df33, mod2)       

# Plot residuals from Scenario 13
par(mfrow=c(2,2))
plot(al_glm3f)

```

```{r, echo=FALSE, eval=FALSE}
# Figure
# BenNear_reg_l # has data through 2015
# df33$prob2 # predicted mussel data

fig1 <- ggplot() + 
        geom_point(data=BenNear_reg_l, aes(x=as.factor(Year), y=mussel_Anom, color=Region), size=4) +
        geom_point(data=df33, aes(x=as.factor(Year), y=prob2, color=Region), shape=17, size=4) + 
        xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                    "2013", "2014", "2015")) +
        theme_bw() + geom_hline(yintercept = 0, show.legend = FALSE)
  #      scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                 "2013", "2014", "2015"))
       
fig1

```

```{r, echo=FALSE}
# Figure

line_dat <- BenNear_reg_cpa %>% 
            select(Year, Region, mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                   Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov) %>%
            group_by(Year) %>%
            mutate(Bare_Sub_mn = mean(Bare_Sub_Per_Cov),
                   Fuc_dist_mn = mean(Fuc_dist_Per_Cov),
                   muss_Anom_mn = mean(mussel_Anom),
                   FWDisc_Yr_mn = mean(FWDisc_MeanYearly_ft3s1)) %>%
            ungroup() %>%
            select(Year, Region, log_TotChlA_micgL_AnnMn, NPGO_anul_mn, Bare_Sub_mn, 
                   Fuc_dist_mn, muss_Anom_mn, FWDisc_Yr_mn) %>%
            gather("Variable", "value", 3:8) %>%
            mutate(facet = ifelse(Variable %in% c("NPGO_anul_mn", "muss_Anom_mn",
                                                  "log_TotChlA_micgL_AnnMn"), "A", 
                           ifelse(Variable %in% c("Fuc_dist_mn", "Bare_Sub_mn"), "B", 
                           ifelse(Variable == "FWDisc_Yr_mn", "C","")))) %>%
            select(Year, Region, Variable, value, facet)

######
fig2 <- ggplot(data=line_dat, aes(x=as.factor(Year), y=value, color=Variable, group=as.factor(Variable))) + 
        geom_line() + facet_wrap(~facet, ncol=1, scale="free") + 
        theme_bw() +
        xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                    "2013", "2014", "2015")) #+
  
fig2

```

##### Trying to get 2014 and 2015 based on generating an "average" freshwater dischange value 
```{r, echo=FALSE, eval=FALSE}
# Trying to get 2014 and 2015 based on generating an "average" freshwater dischange value and using that
# BenNear_reg_l # has data through 2015

k <- mean(BenNear_reg_l$FWDisc_MeanYearly_ft3s1, na.rm = TRUE)

BenNear_reg_klug <- BenNear_reg_l %>%
                    mutate(FWDisc_MeanYearly_ft3s1_klug = ifelse(is.nan(FWDisc_MeanYearly_ft3s1), 
                                                                 9997.097, FWDisc_MeanYearly_ft3s1)) %>%
                    select(mussel_Anom, log_TotChlA_micgL_AnnMn, #FWDisc_MeanYearly_ft3s1, Year, Region,   
                           Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov, 
                           FWDisc_MeanYearly_ft3s1_klug) %>%
                    filter(Year %in% c(2006:2015)) %>%
                    select(-Year, -Region)

#mussel_Anom, log_TotChlA_micgL_AnnMn, SC_Mn_FWDisc_AnMn,
#Bare_Sub_Per_Cov, NPGO_anul_mn, Fuc_dist_Per_Cov

```

```{r, echo=FALSE, eval=FALSE}
####
prob3 <- predict(al_glm2, BenNear_reg_klug)   #prob2 <- predict(al_glm2, BenNear_reg_cpa_sub2a)
df34 <- cbind(BenNear_reg_klug[,c(1:3)], prob3)


# Hand calculate things
#al_glm2$coefficients
mod2 <- al_glm2$model %>%
        mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
               fresh = FWDisc_MeanYearly_ft3s1 * -0.0006520642,
               bare = Bare_Sub_Per_Cov * -0.0443574427,
               NPGO = NPGO_anul_mn * 0.5163426933, 
               Fucs = Fuc_dist_Per_Cov * -0.0135771762,
               inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
        select(chl, fresh, bare, NPGO, Fucs, inter) %>%
        rowSums() 

cbind(df33, mod2)   


qplot(data=df34, as.factor(Year), prob3, color=Region, size=3)
qplot(data=df34, as.factor(Year), mussel_Anom, color=Region, size=3)

```

## Site-level Analysis

```{r, echo=FALSE}

BenNear_site_l <- BenNear_m %>% 
                  select(-Quadrat,-Lat,-Long) %>%
                  group_by(Year, Region, Site_Name) %>%
                  summarise_each(funs(mean(., na.rm=TRUE))) %>%
                  ungroup() %>%
                  arrange(Region, Site_Name, Year) %>%
                  group_by(Site_Name) %>%
                  mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
                 #        LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
                 #       # LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
                 #       # LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
                 #        LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
                 #        LAG_PDO_anul_mn = lag(PDO_anul_mn),
                 #        LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
                 #        LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
                 #        LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
                         LAG_FWDisc_MeanYearly_ft3s1 = lag(FWDisc_MeanYearly_ft3s1)) %>%#,
                 #        LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
                 #        LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
                 #        LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn)) %>%
                  ungroup() 

```

```{r, echo=FALSE}

BenNear_site_cpa <- BenNear_site_l %>%  #filter(Year %in% c("2007","2010","2012","2013")) %>%
                    filter(!(Year == "2007" & Region == "KEFJ")) %>%  # Tom D says don't use this year/region
                    select(-mussel_Per_Cov, 
                           -Ala_marg_Per_Cov, -TotChlA_micgL_AnnMn) %>% 
                    filter(complete.cases(.))

```


```{r, echo=FALSE}
# Run PCA at Site level 
# 
pca_site <- prcomp(~., data=BenNear_site_cpa[,-c(1,2,3,16,17,37,40)], na.action=na.omit, scale=TRUE)
#print(pca_cpa) # shows SDs and weightings
summary(pca_site)

evyload1 <- abs(pca_site$rotation)
evi_per1 <- sweep(evyload1, 2, colSums(evyload1), "/")
evi_per_imp <- data.frame(evi_per1) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
evi_per_imp2 <- data.frame(evi_per1) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
evi_per_imp3 <- data.frame(evi_per1) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
evi_per_imp4 <- data.frame(evi_per1) %>% select(PC4) %>% tibble::rownames_to_column() %>%
               arrange(-PC4)
evi_per_imp5 <- data.frame(evi_per1) %>% select(PC5) %>% tibble::rownames_to_column() %>%
               arrange(-PC5)
evi_per_imp6 <- data.frame(evi_per1) %>% select(PC6) %>% tibble::rownames_to_column() %>%
               arrange(-PC6)
evi_per_imp7 <- data.frame(evi_per1) %>% select(PC7) %>% tibble::rownames_to_column() %>%
               arrange(-PC7)
evi_per_imp8 <- data.frame(evi_per1) %>% select(PC8) %>% tibble::rownames_to_column() %>%
               arrange(-PC8)
evi_per_imp9 <- data.frame(evi_per1) %>% select(PC9) %>% tibble::rownames_to_column() %>%
               arrange(-PC9)
evi_per_imp10 <- data.frame(evi_per1) %>% select(PC10) %>% tibble::rownames_to_column() %>%
               arrange(-PC10)
evi_per_imp ; evi_per_imp2 ; evi_per_imp3 ; evi_per_imp4

par(mfrow=c(1,2))
plot(pca_cpa, main="everything")
plot(pca_cpa, type="lines", main="everything")



# Plotting
pca_site_all <- autoplot(prcomp(BenNear_site_cpa[,-c(1,2,3,16,17,37,41)], scale=TRUE),
                        data=BenNear_site_cpa,  colour='Site_Name', loadings=TRUE,
                        loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=4)
pca_site_all


```


##### Scenario 1 - Site
```{r, echo=FALSE}
##########################
# PCA-informed model

BenNear_site_cpa_sub <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "LAG_FWDisc_MeanYearly_ft3s1", 
                          "FWDisc_MeanYearly_ft3s1", "UpWelAnom_anul_mn", "ENSO_anul_mn",
                          "NPGO_anul_mn", "PDO_anul_mn", "Hobo_WaterTemp_AnnMn", "SOtt_AnnMnEngRec",
                          "Fuc_dist_Per_Cov", "Brwn_alg_ann_Per_Cov", "Green_alg_ann_Per_Cov",
                          "Red_alg_ann_Per_Cov", "Neo_Odon_sp_Per_Cov", "Whelk_Sum_n_m2",
                          "barnacle_Per_Cov", "BLOYAdult_breed_n", "Bare_Sub_Per_Cov")

Sce_1_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub)
Sce_1_s

```

##### Scenario 2 - Site - kitchen sink
```{r, echo=FALSE}

BenNear_site_cpa_sub2 <- c("-Year", "-Region", "-Site_Name", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn",
                           "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn",
                           "-ENSO_spr_mn", "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn",
                           "-WaterTmp_C_Winter", "-WaterTmp_WinterAnom", "-Red_alg_ann_Per_Cov", 
                           "-PDO_anul_mn", "-LAG_log_TotChlA_micgL_AnnMn"
                           )

Sce_2_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2)
Sce_2_s

```

#### Scenario 3 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2l <- c("-Year", "-Region", "-Site_Name", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn",
                            "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn",
                            "-ENSO_spr_mn", "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn",
                            "-WaterTmp_C_Winter", "-WaterTmp_WinterAnom", "-Red_alg_ann_Per_Cov", 
                            "-PDO_anul_mn", "-log_TotChlA_micgL_AnnMn"
                            )

Sce_3_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2l)
Sce_3_s

```

##### Scenario 4 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2pl <- c("-Year", "-Region",  "-Site_Name", "-log_mussel_Per_Cov", "-UpWelAnom_fal_mn",
                             "-UpWelAnom_spr_mn", "-TotChlA_micgL_FlMn", "-log_TotChlA_micgL_FlMn",
                             "-ENSO_spr_mn", "-ENSO_fal_mn", "-PDO_spring_mn", "-PDO_winter_mn",
                             "-Red_alg_ann_Per_Cov", "-WaterTmp_WinterAnom", "-PDO_anul_mn",
                             "-LAG_log_TotChlA_micgL_AnnMn"
                             )

Sce_4_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2pl)
Sce_4_s

```

##### Scenario 5 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2a <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov", 
                            "barnacle_Per_Cov"
                            )

Sce_5_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2a)
Sce_5_s

```

##### Scenario 6 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2al <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "LAG_FWDisc_MeanYearly_ft3s1",
                             "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov"
                             )

Sce_6_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2al)
Sce_6_s

```

##### Scenario 7 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2b <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "Bare_Sub_Per_Cov", "Fuc_dist_Per_Cov",  "Hobo_WaterTemp_AnnMn", 
                            "SOtt_AnnMnEngRec", "BLOYAdult_breed_n", "ENSO_anul_mn",
                            "UpWelAnom_anul_mn", "NPGO_anul_mn"
                            )

Sce_7_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2b)
Sce_7_s

```

##### Scenario 8 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2bb <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "ENSO_anul_mn", 
                             "Fuc_dist_Per_Cov", "Red_alg_per_Per_Cov", "Bare_Sub_Per_Cov", 
                             "UpWelAnom_anul_mn"
                             )

Sce_8_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2bb)
Sce_8_s

```

##### Scenario 9 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2bt <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "Bare_Sub_Per_Cov", "NPGO_anul_mn", "Fuc_dist_Per_Cov", 
                             "Red_alg_per_Per_Cov", "UpWelAnom_anul_mn"
                             )

Sce_9_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2bt)
Sce_9_s

```

##### Scenario 10 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2bw <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "Bare_Sub_Per_Cov", "NPGO_anul_mn", "UpWelAnom_anul_mn", 
                             "Fuc_dist_Per_Cov", "Red_alg_per_Per_Cov", "Whelk_Sum_n_m2",
                             "barnacle_Per_Cov"
                             )

Sce_10_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2bw)
Sce_10_s

```

##### Scenario 11 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2e <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Fuc_dist_Per_Cov", 
                            "Red_alg_per_Per_Cov", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                            )

Sce_11_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2e)
Sce_11_s

```

##### Scenario 12 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2wt <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Fuc_dist_Per_Cov", "Red_alg_per_Per_Cov", 
                             "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                             )

Sce_12_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2wt)
Sce_12_s

```

##### Scenario 13 (from above) ### WINNER at Regional level
```{r, echo=FALSE}

BenNear_site_cpa_sub2f <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                            "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Red_alg_per_Per_Cov", 
                            "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                            )

Sce_13_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f)
Sce_13_s

```

##### Scenario 14 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2fg <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", "Red_alg_TOT_Per_Cov", 
                             "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                             )

Sce_14_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2fg)
Sce_14_s

```

##### Scenario 15 - Site    WINNER!!!
```{r, echo=FALSE}

BenNear_site_cpa_sub2fh <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                             )

Sce_15_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2fh)
Sce_15_s

```

##### Scenario 16 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2f16 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                              "NPGO_anul_mn",  "Red_alg_TOT_Per_Cov", "Bare_Sub_Per_Cov", 
                              "UpWelAnom_anul_mn"
                              )

Sce_16_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f16)
Sce_16_s

```

##### Scenario 17 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2f17 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                              "NPGO_anul_mn",  "Fuc_dist_Per_Cov", "Bare_Sub_Per_Cov", 
                              "UpWelAnom_anul_mn"
                              )

Sce_17_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f17)
Sce_17_s

```

##### Scenario 18 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2f18 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                              "Hobo_WaterTemp_AnnMn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn"
                              )

Sce_18_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f18)
Sce_18_s

```

##### Scenario 19 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2f19 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                              "Bare_Sub_Per_Cov", "SOtt_AnnMnEngRec", "BLOYAdult_breed_n", 
                              "Whelk_Sum_n_m2", "barnacle_Per_Cov"
                              )

Sce_19_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f19)
Sce_19_s

```

##### Scenario 20 - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub2f20 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                              "Bare_Sub_Per_Cov", "SOtt_AnnMnEngRec", "BLOYAdult_breed_n", 
                              "Whelk_Sum_n_m2"
                              )

Sce_20_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub2f20)
Sce_20_s

```

##### Scenario 21 (15 plus preds) - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub221 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn",
                             "SOtt_AnnMnEngRec"
                             )

Sce_21_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub221)
Sce_21_s

```

##### Scenario 22 (15 plus preds) - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub222 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn",
                             "BLOYAdult_breed_n"
                             )

Sce_22_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub222)
Sce_22_s

```

##### Scenario 23 (15 plus preds) - Site
```{r, echo=FALSE}

BenNear_site_cpa_sub223 <- c("mussel_Anom", "log_TotChlA_micgL_AnnMn", "FWDisc_MeanYearly_ft3s1",
                             "NPGO_anul_mn", "Bare_Sub_Per_Cov", "UpWelAnom_anul_mn",
                             "Whelk_Sum_n_m2"
                             )

Sce_23_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_site_cpa_sub223)
Sce_23_s

```


##### Scenario 12 - Transect   WINNER from the Transect-level analysis
```{r, echo=FALSE}

BenNear_tran_cpa_sub2l12_s <- c("mussel_Anom", "log_TotChlA_micgL_FlMn", "FWDisc_MeanYearly_ft3s1", 
                                "SOtt_AnnMnEngRec", "NPGO_anul_mn", "Hobo_WaterTemp_AnnMn", 
                                "BLOYAdult_breed_n", "Bare_Sub_Per_Cov", "Brwn_alg_ann_Per_Cov",
                                "Green_alg_ann_Per_Cov"
                                )

Sce_12t_s <- data_sub_model_run(orig_df=BenNear_site_cpa, select_cols=BenNear_tran_cpa_sub2l12_s)
Sce_12t_s

```

##### AIC values for all Site models
```{r, echo=FALSE}
Site_mod_list <- list(Sce_1_s, Sce_2_s, Sce_3_s, Sce_4_s, Sce_5_s, Sce_6_s, Sce_7_s, Sce_8_s, 
                      Sce_9_s, Sce_10_s, Sce_11_s, Sce_12_s, Sce_13_s, Sce_14_s, Sce_15_s, Sce_16_s,
                      Sce_17_s, Sce_18_s, Sce_19_s, Sce_20_s, Sce_21_s, Sce_22_s, Sce_23_s,
                      Sce_12t_s
                      )

for (i in 1:length(Site_mod_list)) {
     print(Site_mod_list[[i]][[1]])
     }

```

```{r, echo=FALSE, eval=FALSE}
# For Scenario 15
prob3 <- predict(site_glm3fh, BenNear_site_cpa_sub2fh)
df333 <- cbind(BenNear_site_cpa[,c(1,2,3,40)], prob3)

qplot(data=df333, prob3, mussel_Anom, color=Region, size=3)
cor(prob3, BenNear_site_cpa[,40])
#cor(BenNear_reg_cpa_sub2a[,1], BenNear_reg_cpa_sub2a[,3])

# For Scenario 22
prob4 <- predict(site_glm322, BenNear_site_cpa_sub222)
df334 <- cbind(BenNear_site_cpa[,c(1,2,3,40)], prob4)

qplot(data=df334, prob4, mussel_Anom, color=Region, size=3)
cor(prob4, BenNear_site_cpa[40])


# Hand calculate things   # CURRENTLY NOT THE WINNING MODEL 13!  NEEDS TO BE REVISED. 
#al_glm2$coefficients
# mod2 <- al_glm2$model %>%
#         mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
#                fresh = SC_Mn_FWDisc_AnMn * -0.0006520642,
#                bare = Bare_Sub_Per_Cov * -0.0443574427,
#                NPGO = NPGO_anul_mn * 0.5163426933, 
#                Fucs = Fuc_dist_Per_Cov * -0.0135771762,
#                inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
#         select(chl, fresh, bare, NPGO, Fucs, inter) %>%
#         rowSums() 
# 
# cbind(df33, mod2)       

```

```{r, echo=FALSE, eval=FALSE}
# Plotting Residuals to check model fit

resid_site_15 <- site_glm3fh$residuals

par(mfrow=c(2,2))
plot(site_glm3fh)

#
resid_site_22 <- site_glm322$residuals

par(mfrow=c(2,2))
plot(site_glm322)


```

```{r, echo=FALSE, eval=FALSE}
# Figure
# BenNear_site_l # has data through 2015
# df333$prob3 # predicted mussel data for Scenario 15
# df334$prob4 # predicted mussel data for Scenario 22

fig15 <- ggplot() + 
         geom_point(data=BenNear_site_l, aes(x=as.factor(Year), y=mussel_Anom, color=Site_Name), size=4) +
         geom_point(data=df333, aes(x=as.factor(Year), y=prob3, color=Site_Name), shape=17, size=4) + 
         xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                     "2013", "2014", "2015")) +
         theme_bw() + geom_hline(yintercept = 0, show.legend = FALSE)
  #       scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                  "2013", "2014", "2015"))

fig15



fig22 <- ggplot() + 
         geom_point(data=BenNear_site_l, aes(x=as.factor(Year), y=mussel_Anom, color=Site_Name), size=4) +
         geom_point(data=df334, aes(x=as.factor(Year), y=prob4, color=Site_Name), shape=17, size=4) + 
         xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                     "2013", "2014", "2015")) +
         theme_bw() + geom_hline(yintercept = 0, show.legend = FALSE)
  #       scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                  "2013", "2014", "2015"))
        
fig22
```

```{r, echo=FALSE}

fig15a <- ggplot() + 
          geom_point(data=BenNear_site_l, aes(x=as.factor(Year), y=mussel_Anom, color=Site_Name, 
                                              shape=Region), size=4) +
         # geom_point(data=df333, aes(x=as.factor(Year), y=prob3, color=Site_Name), shape=17, size=4) + 
          xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                        "2013", "2014", "2015")) +
          theme_bw() + geom_hline(yintercept = 0, show.legend = FALSE)
  #        scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                   "2013", "2014", "2015"))
        
fig15a

```


## Transect-level Analyses (Within-Site)

```{r, echo=FALSE}

BenNear_tran_l <- BenNear_m %>% 
                  select(-Lat,-Long) %>%
                  arrange(Region, Site_Name, Year, Quadrat) %>%
                  group_by(Site_Name, Quadrat) %>%
                  mutate(LAG_log_TotChlA_micgL_AnnMn = lag(log_TotChlA_micgL_AnnMn),
                         LAG_log_TotChlA_micgL_FlMn = lag(log_TotChlA_micgL_FlMn),
                 #        LAG_UpWelAnom_anul_mn = lag(UpWelAnom_anul_mn),
                 #       # LED_SOf_MusselPropBmss = lead(SOf_MusselPropBmss),
                 #       # LED_BLOYAdult_breed_n = lead(BLOYAdult_breed_n),
                 #        LAG_Bare_Sub_Per_Cov = lag(Bare_Sub_Per_Cov),
                 #        LAG_PDO_anul_mn = lag(PDO_anul_mn),
                 #        LAG_WndSp_m_s_AnnMn = lag(WndSp_m_s_AnnMn),
                 #        LAG_WndSp_m_s_Winter = lag(WndSp_m_s_Winter),
                 #        LAG_Fuc_dist_Per_Cov = lag(Fuc_dist_Per_Cov),
                         LAG_FWDisc_MeanYearly_ft3s1 = lag(FWDisc_MeanYearly_ft3s1)) %>%#,
                 #        LAG_Ttl_FWDisc_Anom_AnMn = lag(Ttl_FWDisc_Anom_AnMn),
                 #        LAG_SC_Mn_FWDisc_SpMn = lag(SC_Mn_FWDisc_SpMn),
                 #        LAG_Ttl_FWDisc_Anom_SpMn = lag(Ttl_FWDisc_Anom_SpMn)) %>%
                  ungroup() 


```

```{r, echo=FALSE}

BenNear_tran_cpa <- BenNear_tran_l %>%  #filter(Year %in% c("2007","2010","2012","2013")) %>%
                    filter(!(Year == "2007" & Region == "KEFJ")) %>%  # Tom D says don't use this year/region
                    select(-mussel_Per_Cov, -TotChlA_micgL_AnnMn,
                           -WaterTmp_SpringAnom, -Ala_marg_Per_Cov) %>% 
                    filter(complete.cases(.))


```

```{r, echo=FALSE}
# Run PCA at Transect level 
# 
pca_tran <- prcomp(~., data=BenNear_tran_cpa[,-c(1,2,3,37,40,42)], na.action=na.omit, scale=TRUE)
#print(pca_cpa) # shows SDs and weightings
summary(pca_tran)

evyload1 <- abs(pca_tran$rotation)
evi_per1 <- sweep(evyload1, 2, colSums(evyload1), "/")
evi_per_imp <- data.frame(evi_per1) %>% select(PC1) %>% tibble::rownames_to_column() %>%
               arrange(-PC1)
evi_per_imp2 <- data.frame(evi_per1) %>% select(PC2) %>% tibble::rownames_to_column() %>%
               arrange(-PC2)
evi_per_imp3 <- data.frame(evi_per1) %>% select(PC3) %>% tibble::rownames_to_column() %>%
               arrange(-PC3)
evi_per_imp4 <- data.frame(evi_per1) %>% select(PC4) %>% tibble::rownames_to_column() %>%
               arrange(-PC4)
evi_per_imp5 <- data.frame(evi_per1) %>% select(PC5) %>% tibble::rownames_to_column() %>%
               arrange(-PC5)
evi_per_imp6 <- data.frame(evi_per1) %>% select(PC6) %>% tibble::rownames_to_column() %>%
               arrange(-PC6)
evi_per_imp7 <- data.frame(evi_per1) %>% select(PC7) %>% tibble::rownames_to_column() %>%
               arrange(-PC7)
evi_per_imp8 <- data.frame(evi_per1) %>% select(PC8) %>% tibble::rownames_to_column() %>%
               arrange(-PC8)
evi_per_imp9 <- data.frame(evi_per1) %>% select(PC9) %>% tibble::rownames_to_column() %>%
               arrange(-PC9)
evi_per_imp10 <- data.frame(evi_per1) %>% select(PC10) %>% tibble::rownames_to_column() %>%
               arrange(-PC10)
evi_per_imp ; evi_per_imp2 ; evi_per_imp3 ; evi_per_imp4

par(mfrow=c(1,2))
plot(pca_cpa, main="everything")
plot(pca_cpa, type="lines", main="everything")



# Plotting
pca_tran_all <- autoplot(prcomp(BenNear_tran_cpa[,-c(1,2,3,17,18,38,42)], scale=TRUE),
                        data=BenNear_tran_cpa,  colour='Site_Name', loadings=TRUE,
                        loadings.colour='blue', loadings.label=TRUE,
                        loadings.label.size=4)
pca_tran_all


```

```{r, echo=FALSE}

##### Scenario 13 Winner from Region-level analysis above
BenNear_reg_cpa_sub2f_t <- BenNear_tran_cpa %>% 
                           select(mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                  NPGO_anul_mn, Hobo_WaterTemp_AnnMn,
                                  Red_alg_per_Per_Cov, 
                                  Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                  )
 
al_glm3f_t <- glm(mussel_Anom ~ ., data=BenNear_reg_cpa_sub2f_t, family=gaussian)
summary(al_glm3f_t)


# Scenario 15 Winner from Site-level analysis above
##### Scenario 15  
BenNear_site_cpa_sub215_t <- BenNear_tran_cpa %>% 
                             select(mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                    NPGO_anul_mn,  
                                    Bare_Sub_Per_Cov, UpWelAnom_anul_mn
                                    )
 
site_glm315_t <- glm(mussel_Anom ~ ., data=BenNear_site_cpa_sub215_t, family=gaussian)
summary(site_glm315_t)

# Scenario 22 co-winner from Site-level analysis above
##### Scenario 22 (15 plus preds)
BenNear_tran_cpa_sub222_t <- BenNear_tran_cpa %>% 
                             select(mussel_Anom, log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                    NPGO_anul_mn,  
                                    Bare_Sub_Per_Cov, UpWelAnom_anul_mn,
                                    BLOYAdult_breed_n
                                    )
 
site_glm322_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub222_t, family=gaussian)
summary(site_glm322_t)


##########################
# Scenario 1 - PCA-informed model

BenNear_tran_cpa_sub <- BenNear_tran_cpa %>%
                        select(mussel_Anom, 
                               log_TotChlA_micgL_AnnMn,  PDO_anul_mn, 
                               log_TotChlA_micgL_FlMn, #ENSO_anul_mn, 
                               UpWelAnom_fal_mn, UpWelAnom_spr_mn, FWDisc_MeanYearly_ft3s1, 
                               SOtt_AnnMnEngRec, NPGO_anul_mn,  
                               WaterTmp_C_AnnMn, Fuc_dist_Per_Cov, Neo_Odon_sp_Per_Cov, 
                               Red_alg_TOT_Per_Cov, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                               Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, Green_alg_ann_Per_Cov,
                               barnacle_Per_Cov)
                       

ev_glm_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub, family=gaussian)
summary(ev_glm_t)

#log_TotChlA_micgL_SpMn,

## Scenario 2 - kitchen sink
BenNear_tran_cpa_sub2 <- BenNear_tran_cpa %>% 
                        select(-Year, -Region, -Site_Name, -Quadrat, -log_mussel_Per_Cov, 
                               -UpWelAnom_fal_mn, -UpWelAnom_spr_mn,
                               -TotChlA_micgL_FlMn, -log_TotChlA_micgL_FlMn, 
                               -ENSO_spr_mn, -ENSO_fal_mn, -PDO_spring_mn, -PDO_winter_mn,
                               -WaterTmp_C_Winter, -WaterTmp_WinterAnom, 
                               -Red_alg_ann_Per_Cov, 
                               -PDO_anul_mn, -LAG_log_TotChlA_micgL_AnnMn
                               )
 
al_glm_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2, family=gaussian)
summary(al_glm_t)

## Scenario 3 
BenNear_tran_cpa_sub2l <- BenNear_tran_cpa %>% 
                          select(mussel_Anom,
                               log_TotChlA_micgL_AnnMn,  PDO_anul_mn, 
                               log_TotChlA_micgL_FlMn, #ENSO_anul_mn, 
                               FWDisc_MeanYearly_ft3s1, UpWelAnom_fal_mn, 
                               SOtt_AnnMnEngRec, NPGO_anul_mn, UpWelAnom_anul_mn, 
                               WaterTmp_C_AnnMn, Fuc_dist_Per_Cov, Neo_Odon_sp_Per_Cov, 
                               Red_alg_TOT_Per_Cov, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                               Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, Green_alg_ann_Per_Cov,
                               barnacle_Per_Cov)
 
al_glm_l_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l, family=gaussian)
summary(al_glm_l_t)

## Scenario 4
BenNear_tran_cpa_sub2l4 <- BenNear_tran_cpa %>% 
                           select(mussel_Anom,
                                  log_TotChlA_micgL_AnnMn, # PDO_anul_mn, #Ttl_FWDisc_Anom_AnMn,
                                  log_TotChlA_micgL_FlMn, #ENSO_anul_mn, 
                                  FWDisc_MeanYearly_ft3s1, UpWelAnom_fal_mn, #UpWelAnom_spr_mn,
                                  SOtt_AnnMnEngRec, NPGO_anul_mn, UpWelAnom_anul_mn, 
                                  WaterTmp_C_AnnMn, Fuc_dist_Per_Cov, Neo_Odon_sp_Per_Cov, 
                                  Red_alg_TOT_Per_Cov, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                  Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, Green_alg_ann_Per_Cov,
                                  barnacle_Per_Cov)
 
al_glm_l4_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l4, family=gaussian)
summary(al_glm_l4_t)


## Scenario 5
BenNear_tran_cpa_sub2l5 <- BenNear_tran_cpa %>% 
                           select(mussel_Anom,
                                  log_TotChlA_micgL_FlMn, FWDisc_MeanYearly_ft3s1,
                                  NPGO_anul_mn, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                  Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov)
                                  
 
al_glm_l5_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l5, family=gaussian)
summary(al_glm_l5_t)


## Scenario 6
BenNear_tran_cpa_sub2l6 <- BenNear_tran_cpa %>% 
                          select(mussel_Anom,
                               log_TotChlA_micgL_FlMn,  FWDisc_MeanYearly_ft3s1, NPGO_anul_mn, 
                               Fuc_dist_Per_Cov,   BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                               Green_alg_ann_Per_Cov
                              )
 
al_glm_l6_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l6, family=gaussian)
summary(al_glm_l6_t)

## Scenario 7
BenNear_tran_cpa_sub2l7 <- BenNear_tran_cpa %>% 
                           select(mussel_Anom,
                                  log_TotChlA_micgL_FlMn, FWDisc_MeanYearly_ft3s1,
                                  NPGO_anul_mn, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                  Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov, 
                                  Whelk_Sum_n_m2)
                                  
 
al_glm_l7_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l7, family=gaussian)
summary(al_glm_l7_t)

## Scenario 8
BenNear_tran_cpa_sub2l8 <- BenNear_tran_cpa %>% 
                           select(mussel_Anom,
                                  log_TotChlA_micgL_FlMn, FWDisc_MeanYearly_ft3s1,
                                  NPGO_anul_mn, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                  Red_alg_TOT_Per_Cov, Green_alg_ann_Per_Cov)
                                  
 
al_glm_l8_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l8, family=gaussian)
summary(al_glm_l8_t)

## Scenario 9
BenNear_tran_cpa_sub2l9 <- BenNear_tran_cpa %>% 
                           select(mussel_Anom,
                                  log_TotChlA_micgL_AnnMn, FWDisc_MeanYearly_ft3s1,
                                  NPGO_anul_mn, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                  Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov)
                                  
 
al_glm_l9_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l9, family=gaussian)
summary(al_glm_l9_t)

## Scenario 10
BenNear_tran_cpa_sub2l10 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, FWDisc_MeanYearly_ft3s1,
                                   NPGO_anul_mn, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   UpWelAnom_anul_mn)
                                  
 
al_glm_l10_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l10, family=gaussian)
summary(al_glm_l10_t)

## Scenario 11
BenNear_tran_cpa_sub2l11 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, UpWelAnom_fal_mn,
                                   FWDisc_MeanYearly_ft3s1, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn, Fuc_dist_Per_Cov, Neo_Odon_sp_Per_Cov, 
                                   Red_alg_TOT_Per_Cov, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov,
                                   barnacle_Per_Cov)
                                  
 
al_glm_l11_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l11, family=gaussian)
summary(al_glm_l11_t)

## Scenario 12   # WINNER
BenNear_tran_cpa_sub2l12 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, 
                                   FWDisc_MeanYearly_ft3s1, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l12_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l12, family=gaussian)
summary(al_glm_l12_t)

## Scenario 13
BenNear_tran_cpa_sub2l13 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, 
                                   FWDisc_MeanYearly_ft3s1, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov)
                                  
 
al_glm_l13_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l13, family=gaussian)
summary(al_glm_l13_t)

## Scenario 14
# Try a biology-only model with the stuff measured at the smallest scale. 
BenNear_tran_cpa_sub2l14 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   Fuc_dist_Per_Cov, Neo_Odon_sp_Per_Cov, 
                                   Red_alg_TOT_Per_Cov, BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   Green_alg_ann_Per_Cov, barnacle_Per_Cov)

al_glm_l14_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l14, family=gaussian)
summary(al_glm_l14_t)

## Scenario 15
BenNear_tran_cpa_sub2l15 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   barnacle_Per_Cov)

al_glm_l15_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l15, family=gaussian)
summary(al_glm_l15_t)

## Scenario 16
BenNear_tran_cpa_sub2l16 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   barnacle_Per_Cov)

al_glm_l16_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l16, family=gaussian)
summary(al_glm_l16_t)


## Scenario 17
BenNear_tran_cpa_sub2l17 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, 
                                   FWDisc_MeanYearly_ft3s1, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l17_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l17, family=gaussian)
summary(al_glm_l17_t)

## Scenario 18
BenNear_tran_cpa_sub2l18 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, 
                                   Hobo_WaterTemp_AnnMn, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l18_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l18, family=gaussian)
summary(al_glm_l18_t)

## Scenario 19
BenNear_tran_cpa_sub2l19 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   FWDisc_MeanYearly_ft3s1, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   barnacle_Per_Cov)

al_glm_l19_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l19, family=gaussian)
summary(al_glm_l19_t)

## Scenario 20
BenNear_tran_cpa_sub2l20 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   FWDisc_MeanYearly_ft3s1, Bare_Sub_Per_Cov, NPGO_anul_mn,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   barnacle_Per_Cov)

al_glm_l20_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l20, family=gaussian)
summary(al_glm_l20_t)

## Scenario 21
BenNear_tran_cpa_sub2l21 <- BenNear_tran_cpa %>%  
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, SOtt_AnnMnEngRec, 
                                   FWDisc_MeanYearly_ft3s1, Bare_Sub_Per_Cov, UpWelAnom_anul_mn,
                                   Brwn_alg_ann_Per_Cov, Whelk_Sum_n_m2, 
                                   barnacle_Per_Cov)

al_glm_l21_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l21, family=gaussian)
summary(al_glm_l21_t)

## Scenario 22   Co-Winner!!
BenNear_tran_cpa_sub2l22 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_FlMn, 
                                   FWDisc_MeanYearly_ft3s1, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l22_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l22, family=gaussian)
summary(al_glm_l22_t)

## Scenario 23   
BenNear_tran_cpa_sub2l23 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   LAG_log_TotChlA_micgL_FlMn, 
                                   FWDisc_MeanYearly_ft3s1, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l23_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l23, family=gaussian)
summary(al_glm_l23_t)

## Scenario 24  
BenNear_tran_cpa_sub2l24 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_AnnMn, 
                                   FWDisc_MeanYearly_ft3s1, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l24_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l24, family=gaussian)
summary(al_glm_l24_t)


## Scenario 25
BenNear_tran_cpa_sub2l25 <- BenNear_tran_cpa %>% 
                            select(mussel_Anom,
                                   log_TotChlA_micgL_AnnMn, 
                                   FWDisc_MeanYearly_ft3s1, SOtt_AnnMnEngRec, NPGO_anul_mn,
                                   Hobo_WaterTemp_AnnMn,  BLOYAdult_breed_n, Bare_Sub_Per_Cov,
                                   Brwn_alg_ann_Per_Cov, Green_alg_ann_Per_Cov
                                   )
                                  
 
al_glm_l25_t <- glm(mussel_Anom ~ ., data=BenNear_tran_cpa_sub2l25, family=gaussian)
summary(al_glm_l25_t)


```

```{r, echo=FALSE}
# For Scenario 12
prob5 <- predict(al_glm_l12_t, BenNear_tran_cpa_sub2l12)
df335 <- cbind(BenNear_tran_cpa[,c(1,2,3,40)], prob5)

qplot(data=df335, prob5, mussel_Anom, color=Site_Name, size=3)
cor(prob5, BenNear_tran_cpa[,40])
#cor(BenNear_reg_cpa_sub2a[,1], BenNear_reg_cpa_sub2a[,3])

# For Scenario 22
prob6 <- predict(al_glm_l22_t, BenNear_tran_cpa_sub2l22)
df336 <- cbind(BenNear_tran_cpa[,c(1,2,3,40)], prob6)

qplot(data=df336, prob6, mussel_Anom, color=Site_Name, size=3)
cor(prob6, BenNear_tran_cpa[,40])

# Hand calculate things   # CURRENTLY NOT THE WINNING MODEL 13!  NEEDS TO BE REVISED. 
#al_glm2$coefficients
# mod2 <- al_glm2$model %>%
#         mutate(chl = log_TotChlA_micgL_AnnMn * 0.8582371582,
#                fresh = SC_Mn_FWDisc_AnMn * -0.0006520642,
#                bare = Bare_Sub_Per_Cov * -0.0443574427,
#                NPGO = NPGO_anul_mn * 0.5163426933, 
#                Fucs = Fuc_dist_Per_Cov * -0.0135771762,
#                inter = 6.4909425827) %>%  # multiply by al_glm2$coefficients
#         select(chl, fresh, bare, NPGO, Fucs, inter) %>%
#         rowSums() 
# 
# cbind(df33, mod2)       

```

```{r, echo=FALSE}
# Plotting Residuals to check model fit

resid_site_12 <- al_glm_l12_t$residuals

par(mfrow=c(2,2))
plot(al_glm_l12_t)


par(mfrow=c(2,2))
plot(al_glm_l22_t)


```

```{r, echo=FALSE}
# Figure
# BenNear_tran_l # has data through 2015
# df335$prob5 # predicted mussel data for Scenario 12



fig12 <- ggplot() + 
         geom_point(data=BenNear_tran_l, aes(x=as.factor(Year), y=mussel_Anom, color=Site_Name), size=4) +
         geom_point(data=df335, aes(x=as.factor(Year), y=prob5, color=Site_Name), shape=17, size=4) + 
         xlim(c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
                                     "2013", "2014", "2015")) +
         theme_bw() + geom_hline(yintercept = 0, show.legend = FALSE)
  #       scale_x_discrete(breaks = c("2006", "2007", "2008", "2009", "2010", "2011", "2012", 
   #                                  "2013", "2014", "2015"))
        
       
fig12


```







