---
title: "Species Presence for GOA Benthic Nearshore"
author: "Rachael Blake"
date: "October 14, 2015"
output:
  html_document:
    theme: united
  pdf_document: default
  word_document: default
---

This looks at the presence of a few species in certain regions, based on what Tom Dean mentioned in the phone call on Oct 12, 2015.  

```{r, include=FALSE}
# This just loads the appropriate packages needed (order does matter):
library(httr)
library(plyr)
library(dplyr)
library(XML)
library(curl)
library(rvest)
library(tidyr)
library(stringr)
```

This loads the data from the AOOS portal.  This is the raw Intertidal Inverts and Algae file.
```{r}
URL_IA <- "https://workspace.aoos.org/published/file/744b4b95-e596-41cc-9419-881165da2864/BenthicNearshoreSystemsInGOA_SOP04_RockyCover_2006to2014_Data_20141015.csv"
IAGet <- GET(URL_IA)
IA1 <- content(IAGet, as='text')
IA <- read.csv(file=textConnection(IA1))
```

This defines which sites are in which region: 
```{r}
PWS_Sites <- c("Galena Bay","Observation Island","Olsen Bay","Port Fidalgo",
               "Simpson Bay","Bettles Bay","Cedar Bay","Esther Passage",
               "Perry Island","Unakwik Inlet","Disk Island","Herring Bay",
               "Herring Bay-Bear Cove","Herring Bay-Southwest","Hogan Bay",
               "Iktua Bay","Johnson Bay","Northwest Bay","Whale Bay")

KATM <- c("Amalik Bay","Kaflia Bay","Kinak Bay", "Kukak Bay","Ninagiak Island",
          "Takli Island")
```

## _Alaria marginata_ presence

This selects records of _Alaria marginata_ at all PWS sites.  
Result: _Alaria_ occurs at Observation Island in 2012 & 2014.
```{r}
A_PWS <- filter(IA, Site_Name %in% PWS_Sites & Species_Name=="Alaria marginata")
```

Shows the first few rows of the data set:
```{r}
head(A_PWS) 
```

Shows the last few rows of the data set:
```{r}
tail(A_PWS)
```

##  _Odonthalia / Neorhodomela sp._ presence

This selects records of the _Odonthalia / Neorhodomela sp._ species complex at all KATM sites.  
NOTE: The _Odonthalia / Neorhodomela sp._ species complex includes four Species_Name values.    
Result: _Odonthalia / Neorhodomela sp._ species complex occurs at least once at all sites during years 2010, 2012, 2013, and 2014.
```{r}
Neo_sp <- c("Neorhodomela oregona","Neorhodomela larix",
            "Odonthalia / Neorhodomela sp.","Odonthalia floccosa")
O_KATM <- filter(IA, Site_Name %in% KATM & Species_Name %in% Neo_sp & 
                     Sample_Year %in% c(2010,2011,2012,2013,2014,2015))
```

Shows the first few rows of the data set: 
```{r}
head(O_KATM) 
```

Shows the last few rows of the data set:
```{r}
tail(O_KATM)
```

Shows which years _Odonthalia / Neorhodomela sp._ occurs.
```{r}
unique(O_KATM$Sample_Year)
```

Shows which sites _Odonthalia / Neorhodomela sp._ occurs. 
```{r}
unique(O_KATM$Site_Name)
```



